---
title: "CFN and CCCN network construction"
author: "Mark Grimes"
date: "1/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

Picking up from Data_Import_and_Clustering, the next tasks are to create a co-cluster correlation network (CCCN); add negative correlation edges proteins modified by different PTMs negatively correlate with each other; generate a cluster-filtered network (CFN) from the CCCN, and compile network attributes and other node properties for graphing networks in Cytoscape.   Functions are in separate documents: 

```{r generate CCCN from PTM clusters}
# Check that the correct pruned cluster list is bening employed
length(eu.sp.sed.gzallt)
 # 838
length(essgzallt)
# Pruned length: 818
# This list was prepared with all data including ratios
# Adjacency matrix:
require(plyr)
gzallt.adj <- rbind.fill.matrix(llply(essgzallt, make.adj.mat))
rownames(gzallt.adj) <- colnames(gzallt.adj)
# dim 7398 7398
gzallt.adj.o <- gzallt.adj[order(rownames(gzallt.adj)), order(colnames(gzallt.adj))]
gzallt.cccn.1 <- gzallt.cor[rownames(gzallt.cor) %in% rownames(gzallt.adj.o), colnames(gzallt.cor) %in% colnames(gzallt.adj.o)]
# Check:
setdiff(rownames(gzallt.adj), rownames(gzallt.cccn.1)) # 0
length(intersect(rownames(gzallt.adj), rownames(gzallt.cor)))  # 7398 all good
# Add in correlation as edge values in adjacency matrix:
gzallt.cccn <- gzallt.cor[intersect(rownames(gzallt.adj.o), rownames(gzallt.cor)), intersect(colnames(gzallt.adj.o), colnames(gzallt.cor))]
identical(rownames(gzallt.cccn), colnames(gzallt.cccn))
# [1] TRUE
dim(gzallt.cccn)
# 7398 7398
gzallt.NA <- which(is.na(gzallt.adj.o), arr.ind = TRUE)
gzallt.cccn <- replace (gzallt.cccn, gzallt.NA, NA)
# remove self loops
if(any(!is.na(diag(gzallt.cccn)))) {diag(gzallt.cccn) <- NA}
## ****
# Option: Limit to a particlar correlation value like this.
# gzallt.cccn.halflim <- replace (gzallt.cccn, abs(gzallt.cccn)<0.5, NA)
#
# Make igraph object, which cannot have NA values, so replace NA with 0
gzallt.cccn0 <- gzallt.cccn
  gzallt.cccn0[is.na(gzallt.cccn0)] <- 0
gzallt.cccn.g <- graph.adjacency(as.matrix(gzallt.cccn0), mode="lower", diag=FALSE, weighted="Weight")
#  
```

## Construct Gene CCCN and CFN


```{r construct CCCN and CFN}
# Construct CCCN for proteins (genes) based on correlations of mod sites: 
#	Check for unique row and column names
any(duplicated(rownames(gzallt.cccn)))		#  FALSE
any(duplicated(colnames(gzallt.cccn)))		#  FALSE
# Make Gene CCCN
# Note: Did this on server for large data set, much faster at ddply step
gzallt.gene.cccn <- data.frame(gzallt.cccn, row.names = rownames(gzallt.cccn), check.rows=TRUE, check.names=FALSE, fix.empty.names = FALSE)
identical(rownames(gzallt.gene.cccn), colnames(gzallt.gene.cccn)) # TRUE 
# Extract the gene names from the PTM names
gzallt.gene.cccn$Gene.Name <- sapply(rownames(gzallt.gene.cccn), function (x) unlist(strsplit(x, " ",  fixed=TRUE))[1])
length(unique(gzallt.gene.cccn$Gene.Name))   # 2913 
any(is.na(gzallt.gene.cccn$Gene.Name)) # F
# gzallt.gene.cccn$Gene.Name[grep("NA", gzallt.gene.cccn$Gene.Name, fixed=TRUE)]
# All genes with NA in the name, e.g. "CTNNA1"
# Use only upper triangle so correlations are not duplicated during the next step
gzallt.gene.cccn[lower.tri(gzallt.gene.cccn)] <- NA	
# ________________________________
# Sum correlations in one dimension, then the other dimension
gzallt.gene.cccn2 <- ddply(gzallt.gene.cccn, .(Gene.Name), numcolwise(function(x) sum(x, na.rm=T)), .progress = "tk")
dim(gzallt.gene.cccn2)	#	2913 7399
any(is.na(gzallt.gene.cccn2$Gene.Name)) # F
# make row names the Gene.Name
rownames(gzallt.gene.cccn2) <- gzallt.gene.cccn2$Gene.Name
# remove Gene.Name column
gzallt.gene.cccn2 <- gzallt.gene.cccn2[, 2:ncol(gzallt.gene.cccn2)]
# Now transform to sum in the other dimention
gzallt.gene.cccn2 <- data.frame(t(gzallt.gene.cccn2))
gzallt.gene.cccn2$Gene <- sapply(rownames(gzallt.gene.cccn2), function (x) unlist(strsplit(x, " ",  fixed=TRUE))[1])
any(is.na(gzallt.gene.cccn2$Gene)) # F
# Sum other dimension
gzallt.gene.cccn3 <- ddply(gzallt.gene.cccn2, .(Gene), numcolwise(function(x) sum(x, na.rm=T)), .progress = "tk")
dim(gzallt.gene.cccn3)  #  2913 2914
any(is.na(gzallt.gene.cccn3$Gene)) # F
# Check row and column names alignment 
print(gzallt.gene.cccn3[1:20, 1:8])
tail(data.frame(gzallt.gene.cccn3$Gene, names(gzallt.gene.cccn3[2:ncol(gzallt.gene.cccn3)])))
# R likes to put dots in column names, which is a problem for ambiguous gene names and gene names with hyphens 
# E.g., Note punctuation missing for "HLA"  "NKX2" "NME1 in column names
gzallt.gene.cccn3$Gene[grep("HLA", gzallt.gene.cccn3$Gene)]
names(gzallt.gene.cccn3)[grep("HLA", names(gzallt.gene.cccn3))]
# 
# Work around this problem (once satisfied that the gene names match). 
names(gzallt.gene.cccn3)[2:ncol(gzallt.gene.cccn3)] <- gzallt.gene.cccn3$Gene
rownames(gzallt.gene.cccn3) <- gzallt.gene.cccn3$Gene
identical (rownames(gzallt.gene.cccn3), names(gzallt.gene.cccn3[,2:ncol(gzallt.gene.cccn3)])) # TRUE
# ________________________________
# Make a adjacency matrix with NAs to index edges only for genes that co-cluster
gzallt.gene.cccn0 <- gzallt.gene.cccn3[,2:ncol(gzallt.gene.cccn3)]
# Replace 0 with NA
gzallt.gene.cccn.na <- zero.to.NA(gzallt.gene.cccn0)
# Check
gzallt.gene.cccn.na[1:20, 1:8]
hist(unlist(gzallt.gene.cccn.na), breaks=1000, col="red", echo=FALSE)
hist(unlist(gzallt.gene.cccn0), breaks=1000, col="blue", ylim=c(0, 1200), echo=FALSE)
# Make igraph object
gzallt.gene.cccn.g <- graph.adjacency(as.matrix(gzallt.gene.cccn0), mode="lower", diag=FALSE, weighted="Weight")
#  Check for identical edge attributes
hist(edge_attr(gzallt.gene.cccn.g)[[1]], breaks=1000, col="deepskyblue", ylim=c(0,1200), echo=FALSE)
# to get the adjacency matrix back, but NOTE, edges are 0 or 1.
# gzallt.gene.cccn.mat <- as_adjacency_matrix(gzallt.gene.cccn.g, type="both")
# ________________________________
# Here is how to make an edge list file
gzalltgenecccn.edges <- data.frame(as_edgelist(gzallt.gene.cccn.g))
names(gzalltgenecccn.edges) <- c("Gene.1", "Gene.2")
gzalltgenecccn.edges$Weight <- edge_attr(gzallt.gene.cccn.g)[[1]]
gzalltgenecccn.edges$interaction <- "correlation" 
gzalltgenecccn.edges $interaction[gzalltgenecccn.edges$Weight<=-0.5] <- "negative correlation"
gzalltgenecccn.edges $interaction[gzalltgenecccn.edges$Weight>=0.5] <- "positive correlation"
# dim 60282     4
# 
#######################################################################```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

#  
```

## Get PPI edges and filter them for CFN

```{r construct CCCN and CFN}
# Obtain all PPIs for genes in data from several sources
# To compare the original lung cancer data set to this data set, combine all the gene names
ldgenes <- get.gene.names.from.peps(rownames(ld.ratio.lim.log2))
# 4221 genes
gzgenes <- get.gene.names.from.peps(rownames(kglog2data))
# 1471 genes
# Note: Now include genes that were only detected in one experiment
gzallgenes <- unique(get.gene.names.from.peps(rownames(gzdata.all)))
# 4054 genes
length(intersect(ldgenes, gzgenes))  # 1003
length(intersect(ldgenes, gzallgenes)) # 2138
combinedgenes <- unique (c(ldgenes, gzallgenes))  # 6137
#________________________________________
library(STRINGdb)
# 		Designate local directory in advance of the following
# 
string_db <- STRINGdb$new( version="10", species=9606, score_threshold=0, input_directory="" )	
string_proteins <- string_db$get_proteins()
# dim 20457     4
# Do the whole thing
#
combined.str.ids <- string_db$mp(combinedgenes)
combined.str.net <- string_db$get_interactions(combined.str.ids)
# dim  541585     16; all: 807803     16
#	convert to HUGO gene name format 
# 	duplicates require match function 
combined.str.net$Gene.1 <- sapply(combined.str.net$from, function(x) string_proteins[match(x, string_proteins$protein_external_id), "preferred_name"])
combined.str.net$Gene.2 <- sapply(combined.str.net$to, function(x) string_proteins[match(x, string_proteins$protein_external_id), "preferred_name"])
# combined_score ranges from 150 to 1000
# experiments is from BIND, DIP, GRID, HPRD, IntAct, MINT, and PID.
# 	database is from Biocarta, BioCyc, GO, KEGG, and Reactome.
#	transferred means extrapolated from other species
#    note: some of these duplcate Pathway Commons sources
dim(combined.str.net[combined.str.net$experiments>0,])
# [1] 49327    18; [2] 63871    18
dim(combined.str.net[combined.str.net$experiments_transferred>0,])
# [1] 195352    18; [2] 298450     18
str.e <- combined.str.net[combined.str.net$experiments>0,]
str.et <- combined.str.net[combined.str.net$experiments_transferred>0,]
str.d <- combined.str.net[combined.str.net$database>0,]
str.dt <- combined.str.net[combined.str.net$database_transferred>0,]
combined.str <- unique(rbind (str.e, str.et, str.d, str.dt))  # 251613 edges; 374352 v2
combined.str$edgeType <- "STRINGdb"
combined.str[combined.str$database>0, "edgeType"] <- "database"
combined.str[combined.str$database_transferred>0, "edgeType"] <- "database"
combined.str[combined.str$experiments>0, "edgeType"] <- "experiments"
combined.str[combined.str$experiments_transferred>0, "edgeType"] <- "experiments"
combined.str$Weight <- rowSums(combined.str[, c("experiments", "experiments_transferred", "database", "database_transferred")])
range(combined.str$Weight)  # 43 to 2859
range(log(combined.str$Weight))  #  3.761200 7.958227
combined.str.edges <- combined.str[,c("Gene.1", "Gene.2", "Weight", "edgeType")]
# To make them on the same scale as other dbs:
combined.str.edges$Weight <- combined.str.edges$Weight/1000	
# ****  edges range(combined.str.edges$Weight) 0.043 2.859
save(ldgenes, gzallgenes, combinedgenes, combined.str, combined.str.edges, combined.str.ids, combined.str.net,  file=paste(pcpath, "GZ_PPI_Networks2.RData", sep=""))
#-------------------------	
#  GeneMANIA Cytoscape app has the ability to export network as text in the Results panel. Manually duplcate the file and delete all but the PPIs for
gmfilename <- "Combined_GeneMANIA_PPIs2.txt"
#cat(combinedgenes)
# 
combined.GM.net <- read.table(paste(pcpath, gmfilename, sep=""), header=TRUE, sep = "\t", comment.char = "#", na.strings='', quote = "", stringsAsFactors=FALSE, fill=TRUE)
# dim 567994  6; [2] 1009527      5
# combined.GM.net <- combined.GM.net[, 1:5]
# combined.GM.edges <- get.GM.edgefile(paste(pcpath, gmfilename, sep=""), combinedgenes)
# dim  550380      4; [2] 686055      4
#  	 The following GM names do not match  
# CCNA2 CCNB1 CDK4 CKS2 ILK RPA3 RPL32 SRPK1 TUBG1 UPF2 VCAM1 CUL4A ETF1 NHP2 PJA2 POLR2E rcl SNRPD2 SUZ12 UBC RNF2
# range(combined.GM.net$Weight)
# [1] 7.509860e-08 6.920997e-01
# last edge ZRANB2  TRA2B
# Note: in Cytoscape only the following edges should be included; otherwise edit manually or here.
unique(combined.GM.net$Type)
#  "Genetic Interactions"  "Pathway" "Physical Interactions" "Predicted"   
# Note also that Genetic Interactions may be indirect, and may be excluded for some purposes.
combined.GM.edges <- combined.GM.net
names(combined.GM.edges)[4] <- "edgeType"
# *****
#------------------------------------------
# Update Pathway Commons database
# Pathway commons retrieved from http://www.pathwaycommons.org/archives/PC2/v9/
# pcname <- "PathwayCommons9.All.hgnc.txt"
# New version 11 https://www.pathwaycommons.org/archives/PC2/v11/
pcname <- "PathwayCommons11.All.hgnc.txt"
pcpath <- "/Volumes/Terra_Byte/R_Archive_2/PC_BioPlex/"
pcpath <- "/Users/mark_grimes/Software\ Images/" # Laptop
# load v9 version
# load(file=paste(pcpath,"pcommons_2018.RData", sep=""))
load(file=paste(pcpath,"pcommons_2019.RData", sep=""))
pcfile <- paste(pcpath, pcname, sep="")
pcommons <- read.table(pcfile, header=TRUE, sep = "\t", comment.char = "#", na.strings='', stringsAsFactors=FALSE, fill=TRUE)
# Dim  1014008       7
unique(pcommons$INTERACTION_DATA_SOURCE[grep("PhosphoSite", pcommons$INTERACTION_DATA_SOURCE)])
# Note: Now Contains PSP info
unique(pcommons$INTERACTION_DATA_SOURCE[grep("lex", pcommons$INTERACTION_DATA_SOURCE)])
# But does not contain BioPlex info.
# Now contains interactions with DNA, RNA, and transcription complexes
names(pcommons)
unique(pcommons$INTERACTION_TYPE)
head(pcommons[grep("DnaReference", pcommons$INTERACTION_TYPE),1:6])
head(pcommons[grep("RnaReference", pcommons$INTERACTION_TYPE),1:6])
head(pcommons[grep("ProteinReference", pcommons$INTERACTION_TYPE),1:6])
# Note the format is different 
head(pcommons[grep(";", pcommons$PARTICIPANT_B),1:6])
# But the DNA and RNA interactions can be excluded using 
head(pcommons[-grep(";", pcommons$PARTICIPANT_B),1:6])
# There are also metabolites and chemical compounds
head(pcommons[grep("reacts-with" , pcommons$INTERACTION_TYPE),1:6])
head(pcommons[grep("used-to-produce" , pcommons$INTERACTION_TYPE),1:6])
head(pcommons[grep("consumption-controlled-by" , pcommons$INTERACTION_TYPE),1:6])
head(pcommons[grep("chemical-affects" , pcommons$INTERACTION_TYPE),1:6])
head(pcommons[grep("controls-production-of", pcommons$INTERACTION_TYPE),1:6])
# These have names in the format CHEBI:NNNN for compounds.
# There is no longer "neighbor-of"
head(pcommons[grep("neighbor" , pcommons$INTERACTION_TYPE),1:6])
# Convert to Formatting of PPI edge files used in my functions is
# "Gene.1"   "Gene.2"   "Weight"   "edgeType"
# But note that Cytoscape now likes the edge names to be
# "source"     "target"  "Weight"  "interaction"
# So this will have to be converted for graphing in Cytoscape
pcnet <- pcommons[-grep("CHEBI:", pcommons$PARTICIPANT_A),1:4]
pcnet <- pcnet[-grep("CHEBI:", pcnet$PARTICIPANT_B),]
# Add an arbitrary Weight and rearrange to be consistent with other PPI networks
pcnet$Weight <- 0.2
pcnet <- pcnet[, c(1,3,5,2,4)]
names(pcnet) <- c("Gene.1", "Gene.2", "Weight", "edgeType", "Source")
# now dim 633126      5 (v9);  594752      5 (v11) 
# NOTE: still includes gene and mRNA interactions, which may be useful later
# save(pcnet, file=paste(comp_path,"Dropbox/_Work/R_/pcnet.RData", sep=""))
# ________________________________#________			
#  New Network
#  		BioPlex: Huttlin et al., 2015, Cell 162, 425–440
#		parameters: incorrect ID (p(Wrong)=pW), background (p(NoInt)=pNI), or a true interactor (p(Int)=pInt) 

bpfilename <- "/Volumes/Terra_Byte/R_Archive_2/PC_BioPlex/BioPlex_interactionList_v4.tsv"
bioplex <- read.table(bpfilename, header=TRUE, sep = "\t", comment.char = "", na.strings='', stringsAsFactors=FALSE, fill=TRUE)
# 56553 edges; pInt values range from 0.75 to 1.00
bioplex <- bioplex[,c("SymbolA", "SymbolB", "pInt")]
names(bioplex) <- c("Gene.1", "Gene.2", "Weight")
bioplex$edgeType <- "BioPlex"
save(pcommons, bioplex, pcnet, enzsub, file=paste(pcpath,"pcommons_2019.RData", sep=""))
#_______________________________________________________________
# Karen's enzyme substrate data
enzsubname <- "iptmnet4.1_enzyme_substrate_relations_scored_simpler.txt"
enzsubfile <- paste("_LINCS/_KarenGuolin/", enzsubname, sep="")
enzsub <- read.table(enzsubfile, header=TRUE, sep = "\t", comment.char = "#", na.strings='', stringsAsFactors=FALSE, fill=TRUE)
# Rearrange and rename to conform to standard format
enzsub <- enzsub[,c(3,2,4,1)]
enzsub$Source <- "IP"
names(enzsub) <- c("Gene.1", "Gene.2", "Weight", "edgeType", "Source")
#_______________________________________________________________
# Note also include kinase substrate dataset from PhosphoSite
head(kinsub)
#________			
# Now do Pathway Commons and Bioplex	
combined.pc.edges <- filter.edges.0(combinedgenes, pcnet)  # 119255 edges	
combined.bp.edges <- filter.edges.0(combinedgenes, bioplex)  # 6328 edges
# combined.bp.edges <- combined.bp.edges[,c(1,2,4,3)]
combined.enzsub.edges <- filter.edges.0(combinedgenes, enzsub)  # 4210 edges	
# 
combined.kinsub.edges <- filter.edges.0(combinedgenes, kinsub) # 4086 edges; 4428 with 2019 kinsub
# Make and "all ppi edge" file for comparisone
combined.all.ppi <- rbind(combined.enzsub.edges[,1:4], combined.pc.edges[,1:4], combined.bp.edges, combined.GM.edges[,1:4], combined.str.edges, combined.kinsub.edges)
# 1572925 edges!  1577353 with new kinsub
combined.all.ppi.g <- graph_from_data_frame(combined.all.ppi)
#   927576 edges; 1009527 with kinsub

# Make CFN with PPI edges
# Test whether combined.all.ppi from KGFunDataObjects.RData covers the genes
gzallt.genes.1 <- unique(c(gzalltgenecccn.edges$Gene.1, gzalltgenecccn.edges$Gene.2))
combined.ppi.genes <- unique(c(combined.all.ppi$Gene.1, combined.all.ppi$Gene.2))
leftover <- setdiff(gzallt.genes.1, combined.ppi.genes)  


```
