---
title: "Cluster Enrichment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_packages}
library(devtools)
library(RCy3)
library(plyr)
library(dplyr)
library(RColorBrewer)
library(gplots)
library(igraph)
library(knitr)
library("BiocStyle")
options(stringsAsFactors=FALSE)

# Note: Start Cytoscape
# ------------------------------------------------------------------------
cytoscapePing ()
cytoscapeVersionInfo ()
#if (!cytoscapePing()=="You are connected to Cytoscape!") {
#     print("Turn on Cytoscape to load New_RCy3_Functions.R")}
```

```{r load data objects and functions}
data_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/TenPTMAnalysis/TenCellLineNetwork-Rfiles2/Rfiles/"
code_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/PTMs-to-CCCN-and-CFN/"
load(file=paste(data_path, "KGFunDataObjects-3.RData", sep=""))
load(file=paste(data_path, "LC_TMT_Nets.RData", sep=""))
load(file=paste(data_path, "TenCell-TKI.RData", sep=""))
load(file=paste(data_path, "GZ_PPI_Networks2.RData", sep="")) #has gz.cf w/12461 rows and gz.cf.pruned w/9701
load(file=paste(data_path, "LD_NewCFNCCCN_Networks.RData", sep=""))
load(file=paste(data_path,"drug_effects.RData", sep=""))
load(file=paste(data_path,"BioPlanetNetworks.RData", sep=""))
	source(paste(code_path, "Data_Input_Formatting.R", sep=""))
	#source(paste(code_path, "Dissimilarity_Calculations.R", sep=""))
	source(paste(code_path, "Generate_CCCN_CFN.R", sep=""))
  source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))

```

```{r plot full cfn and cccn}
#Plot the full cfn and cccn. Once this is done in a Cytoscape session, it will not be necessary to run all.ratio.styles() on each smaller subnetwork

full_network <- graph.cfn.cccn.title(gzallt.physical.network, ld=FALSE, gz=TRUE, only.cfn=FALSE, pruned=FALSE, custom.title = "CFN plus CCCN, Physical Interactions")
all.ratio.styles()

```


## Cluster Enrichment Analysis

This analysis will be done for each drug/cell-line combo. When replicates are available, we will select sites that changed at least 2.25-fold in the same direction in at least two experiments. These are the drug/cell line combos:
H3122/Crizotinib: 5 experiments
HCC78/Crizotinib: 2 experiments
H2228/Crizotinib: 1 experiment
STE.1/Crizotinib: 1 experiment

PC9/Erlotinib: 5 experiments
HCC4006/Erlotinib: 1 experiment
HCC827/Erlotinib: 1 experiment

H3122/PR1: 3 experiments
PC9/PR1: 3 experiments

H1781/Afatinib: 1 experiment

H2286_Dasatinib: 1 experiment
H366_Dasatinib: 1 experiment

For each experiment (drug/cell-line combo):
1. Get the list of significantly changed sites

2. Map the sites to clusters

3. Using the same methods as for the all site data, tally the number of sites in the experimental data in each cluster. Then caluclate the number of sites that are not in each cluster.

4. Perform a one-sided Fisher test to look for clusters with more significantly changed sites than expected by chance. To improve the statistical power (limit the number of tests), only do the analysis on clusters that have at least three significantly changed sites. 

## Count the number of sites in each cluster
Here we will compute the number of sites in each cluster in the CCCN. This data will be used as the "background" for enrichment analysis. To do this, we will use the file sites_by_cluster.txt that lists each site in the CCCN in one column and the cluster it belongs to in a second column. We will use the count function in the plyr package to count the number of rows (sites) for each cluster. (This function will create a new dataframe with one column containing the cluster names and the second column containing the number of rows (sites) for each cluster. Then, for each cluster calculate the number of sites in the CCCN that are not in the cluster--the will be the total sites in the CCCN minus the number of sites in the cluster. 

```{r tally_clusters}

#Load the file with the cluster assignments for each site
CCCN_sites_file <- paste(data_path,"sites_by_cluster.txt", sep="")
CCCN_sites <- read.table(CCCN_sites_file, sep = "\t", stringsAsFactors = F, header=T)

#Tally the number of sites in each cluster
all_tally <- plyr::count(CCCN_sites, var = "Cluster")
colnames(all_tally)[2] <- "AllNumInCluster"


#Now calculate the number of unique sites that are not in each family. First find the total number of sites. Then
#subtract the number in each cluster from the total to find the number not in each cluster
num_sites <- nrow(CCCN_sites)
all_tally$AllNumOutCluster <- num_sites - all_tally$AllNumInCluster

```


## Function to Get Significantly Changed Sites

```{r get_sig_sites}

#The function get.sig.sites takes a list of columns from gz.cf (assumes that the column list is "id", "Gene.Name", and then the ratio columns for the desired drug/cell line combo), a threshold fold-change, and a minimum experiment number and returns a dataframe with the id, gene name, and values for sites that are changed by at least the threshold in the same direction in at least the minimum specified number of experiments. If the total number of ratio columns is less than the specified minimum, then it will return sites that meet the threshold for all of the given ratio columns. For example, if num_exp = 3, but there are only two ratio colums given, the function will return sites which are changed by at least the threshold in both of the ratio columns.

get.sig.sites <- function(site_df = gz.cf, columns, threshold = 2.25, num_exp = 2) {
  #Remove gene lines from gz.cf
  gz.cf.sites <- gz.cf[which (gz.cf$Node.ID == "peptide"), ]
  #Make a smaller version of gz.cf with only the site, gene, and desired ration columns
  gz.cf.selected <- gz.cf.sites[columns]
  #Count sites that meet the threshold (up or down)
  gz.cf.selected$count_up <- rowSums(gz.cf.selected[3:length(columns)] > log2(threshold))
  gz.cf.selected$count_down <- rowSums(gz.cf.selected[3:length(columns)] < -log2(threshold))
  num_ratio_cols <- length(columns) - 2
  if (num_ratio_cols < num_exp) {
    #Require that threshold be met for all ratio columns
    selected.sig.sites <- gz.cf.selected[which((gz.cf.selected$count_down == num_ratio_cols) | (gz.cf.selected$count_up == num_ratio_cols)),]
  } else {
    #Require that the threshold be met for at least the number of ratio columns specified in num_exp
    selected.sig.sites <- gz.cf.selected[which((gz.cf.selected$count_down > (num_exp - 1)) | (gz.cf.selected$count_up > (num_exp - 1))),]
  }
  
  return(selected.sig.sites) }

```

## Function to Perform the Enrichment Analysis
```{r cluster_enrichment_function}

#This function takes a dataframe showing which sites are in which clusters, a dataframe of significantly changed sites, and a dataframe with a count of how many sites are in (and not in) each cluster. It maps the sites to clusters, tallies the number of sig sites in each cluster (and not in each cluster), and performs the fisher test. Returns a dataframe with the values used for the fisher 2x2 contingency table, the raw p-value, and the Benjamini corrected p-value.

cluster_enrichment <- function(clusters, sig_sites, all_sites_tally) {
    #Change name of id column of sig_sites table to "Site" so it can be merged with the clusters table
    colnames(sig_sites)[1] = "Site" 

    #To map the sig sites to clusters do a merge of the sig_sites to the clusters table. 
    #Note that some of the sig sites do not map to a cluster, so the number of rows in the merged table is less than the number
    #in the sig sites table
    mapped_sites <- merge(clusters, sig_sites, by = "Site")

    #Calculate the number of selected sites in each cluster
    selected_tally <- plyr::count(mapped_sites, var = "Cluster")
    colnames(selected_tally)[2] <- "SelectedNumInCluster"

    #Calculate the number of selected sites not in each cluster. 
    num_selected_sites <- nrow(mapped_sites)
    selected_tally$SelectedNumOutCluster <- num_selected_sites - selected_tally$SelectedNumInCluster

    #Merge the data for all clusters and the data for the selected clusters. Calculate the other two values needed for
    #the 2x2 contingency table: the non-significant sites that are in the cluster (NotSelectedNumInCluster) and
    #the non-significant sites that are not in the cluster (NotSelectedNumOutCluster). Remove the two all cluster
    #columns (AllNumInCluster and  AllNumOutCluster) so only the 4 columns needed for the contingency table remain.
    #Set the row names to be the cluster ID's. Remove rows where the number of selected sites in a cluster
    #is less than 3 because this is unlikely to give a significant result and will just drive up the number of tests
    fisher_table <- merge(selected_tally, all_sites_tally, by = "Cluster")
    fisher_table$NotSelectedNumInCluster <- fisher_table$AllNumInCluster - fisher_table$SelectedNumInCluster
    fisher_table$NotSelectedNumOutCluster <- fisher_table$AllNumOutCluster - fisher_table$SelectedNumOutCluster
    fisher_table$AllNumInCluster <- NULL
    fisher_table$AllNumOutCluster <- NULL
    rownames(fisher_table) <- fisher_table$Cluster
    fisher_table$Cluster <- NULL
    fisher_table <- fisher_table[ which(fisher_table$SelectedNumInCluster >= 3),]
    
    
    #Perform the Fisher Test and the Benjamini-Hochberg multiple testing correction
    fisher_table$p_value <- apply(fisher_table,1, function(x) fisher.test(matrix(x,nr=2), alternative = "greater")$p.value)
    fisher_table$corr_p_value <- p.adjust(fisher_table$p_value, method = "BH")

    #Add a column with the ratio of selected sites to the ratio of total sites for each cluster
    fisher_table$SelectedToAllRatio <- fisher_table$SelectedNumInCluster/(fisher_table$SelectedNumInCluster + fisher_table$NotSelectedNumInCluster)
    #Sort by corrected p-value
    fisher_table <- fisher_table[order(fisher_table$corr_p_value),]
  
    return(fisher_table)
}



```

## Perform the Enrichment Analysis on Each Drug/Cell Line Combo
```{r process_sig_site_data}

#For each experiment, identify the significant sites, write list of sig sites to a file, and perform the enrichment
sig_site_file_path = "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/ClusterEnrichment/ClusterEnrichmentCytoscapeFiles/SigSites/"

#H3122/Crizotinib
h3122.criz.columns <- c("id", "Gene.Name", "H3122SEPTM.C1.ratio", "H3122SEPTM.C2.ratio", "H3122SEPTM.C3.ratio", "H3122_Crizotinib.1Ratio", "H3122CrizotinibRatio")
h3122.criz.sig.sites <- get.sig.sites(columns = h3122.criz.columns)
nrow(h3122.criz.sig.sites)
write.table(h3122.criz.sig.sites, file = paste(sig_site_file_path, "H3122-Crizotinib-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
h3122.criz.enrich <- cluster_enrichment(CCCN_sites, h3122.criz.sig.sites, all_tally)

#HCC78/Crizotinib
hcc78.criz.columns <- c("id", "Gene.Name", "HCC78_Crizotinib.1Ratio", "HCC78_CrizotinibRatio")
hcc78.criz.sig.sites <- get.sig.sites(columns = hcc78.criz.columns)
nrow(hcc78.criz.sig.sites)
write.table(hcc78.criz.sig.sites, file = paste(sig_site_file_path, "HCC78-Crizotinib-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
hcc78.criz.enrich <- cluster_enrichment(CCCN_sites, hcc78.criz.sig.sites, all_tally)

#H2228/Crizotinib
h2228.criz.columns <- c("id", "Gene.Name", "H2228CrizotinibRatio")
h2228.criz.sig.sites <- get.sig.sites(columns = h2228.criz.columns)
nrow(h2228.criz.sig.sites)
write.table(h2228.criz.sig.sites, file = paste(sig_site_file_path, "H2228-Crizotinib-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
h2228.criz.enrich <- cluster_enrichment(CCCN_sites, h2228.criz.sig.sites, all_tally)

#STE1/Crizotinib
ste1.criz.columns <- c("id", "Gene.Name", "STE.1_CrizotinibRatio")
ste1.criz.sig.sites <- get.sig.sites(columns = ste1.criz.columns)
nrow(ste1.criz.sig.sites)
write.table(ste1.criz.sig.sites, file = paste(sig_site_file_path, "STE1-Crizotinib-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
ste1.criz.enrich <- cluster_enrichment(CCCN_sites, ste1.criz.sig.sites, all_tally)

#PC9/Erlotinib
pc9.erl.columns <- c("id", "Gene.Name", "PC9SEPTM.E1.ratio", "PC9SEPTM.E2.ratio", "PC9SEPTM.E3.ratio", "PC9_Erlotinib.1Ratio", "PC9_ErlotinibRatio")
pc9.erl.sig.sites <- get.sig.sites(columns = pc9.erl.columns)
nrow(pc9.erl.sig.sites)
write.table(pc9.erl.sig.sites, file = paste(sig_site_file_path, "PC9-Erlotinib-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
pc9.erl.enrich <- cluster_enrichment(CCCN_sites, pc9.erl.sig.sites, all_tally)

#HCC4006/Erlotinib
hcc4006.erl.columns <- c("id", "Gene.Name", "HCC4006_ErlotinibRatio")
hcc4006.erl.sig.sites <- get.sig.sites(columns = hcc4006.erl.columns)
nrow(hcc4006.erl.sig.sites)
write.table(hcc4006.erl.sig.sites, file = paste(sig_site_file_path, "HCC4006-Erlotinib-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
hcc4006.erl.enrich <- cluster_enrichment(CCCN_sites, hcc4006.erl.sig.sites, all_tally)

#HCC827/Erlotinib
hcc827.erl.columns <- c("id", "Gene.Name", "HCC827_ErlotinibRatio")
hcc827.erl.sig.sites <- get.sig.sites(columns = hcc827.erl.columns)
nrow(hcc827.erl.sig.sites)
write.table(hcc827.erl.sig.sites, file = paste(sig_site_file_path, "HCC827-Erlotinib-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
hcc827.erl.enrich <- cluster_enrichment(CCCN_sites, hcc827.erl.sig.sites, all_tally)

#H3122/PR
h3122.pr.columns <- c("id", "Gene.Name", "H3122SEPTM.PR1.ratio", "H3122SEPTM.PR2.ratio", "H3122SEPTM.PR3.ratio")
h3122.pr.sig.sites <- get.sig.sites(columns = h3122.pr.columns)
nrow(h3122.pr.sig.sites)
write.table(h3122.pr.sig.sites, file = paste(sig_site_file_path, "H3122-PR-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
h3122.pr.enrich <- cluster_enrichment(CCCN_sites, h3122.pr.sig.sites, all_tally)

#PC9/PR
pc9.pr.columns <- c("id", "Gene.Name", "PC9SEPTM.PR1.ratio", "PC9SEPTM.PR2.ratio", "PC9SEPTM.PR3.ratio")
pc9.pr.sig.sites <- get.sig.sites(columns = pc9.pr.columns)
nrow(pc9.pr.sig.sites)
write.table(pc9.pr.sig.sites, file = paste(sig_site_file_path, "PC9-PR-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
pc9.pr.enrich <- cluster_enrichment(CCCN_sites, pc9.pr.sig.sites, all_tally)

#H1781/Afatinib
h1781.afat.columns <- c("id", "Gene.Name", "H1781_AfatinibRatio")
h1781.afat.sig.sites <- get.sig.sites(columns = h1781.afat.columns)
nrow(h1781.afat.sig.sites)
write.table(h1781.afat.sig.sites, file = paste(sig_site_file_path, "H1781-afat-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
h1781.afat.enrich <- cluster_enrichment(CCCN_sites, h1781.afat.sig.sites, all_tally)

#H2286/Dasatinib
h2286.dasat.columns <- c("id", "Gene.Name", "H2286_DasatinibRatio")
h2286.dasat.sig.sites <- get.sig.sites(columns = h2286.dasat.columns)
nrow(h2286.dasat.sig.sites)
write.table(h2286.dasat.sig.sites, file = paste(sig_site_file_path, "H2286-dasat-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
h2286.dasat.enrich <- cluster_enrichment(CCCN_sites, h2286.dasat.sig.sites, all_tally)

#H366/Dasatinib
h366.dasat.columns <- c("id", "Gene.Name", "H366_DasatinibRatio")
h366.dasat.sig.sites <- get.sig.sites(columns = h366.dasat.columns)
nrow(h366.dasat.sig.sites)
write.table(h366.dasat.sig.sites, file = paste(sig_site_file_path, "H366-dasat-sig-sites.txt", sep=""), sep = "\t", quote = FALSE, row.names=FALSE)
h366.dasat.enrich <- cluster_enrichment(CCCN_sites, h366.dasat.sig.sites, all_tally)
```

## Make a Table Showing Clusters that Meet a p-value Threshold for Each Drug/Cell Line Combo
```{r make_all_result_table}

format_enrichment_table <- function(enrich_table, col_name, p_value) {
  #Cluster names are currently the row names. Make the cluster names the first column and delete the row names.
  #Name the new first column with the cluster names "Cluster"
  enrich_table <- cbind(rownames(enrich_table), data.frame(enrich_table, row.names=NULL))
  colnames(enrich_table)[1] <- "Cluster"
  
  #Select just the Cluster and corr_p_value columns.
  #Select the rows where the corr_p_value is less than the threshold p-value
  #Change name of corr_p_value column to col_name
  enrich_table <- enrich_table[c("Cluster", "corr_p_value")]
  enrich_table <- enrich_table[which (enrich_table$corr_p_value <  p_value), ]
  colnames(enrich_table)[2] <- col_name
  
  return(enrich_table)
}

#Run the formatting function on the enrichment results for all 12 drug-cell-line combos and then join into one big table

h3122.criz.enrich.format <- format_enrichment_table(h3122.criz.enrich, "h3122.criz", p_value = 0.01)
all_results <- h3122.criz.enrich.format

hcc78.criz.enrich.format <- format_enrichment_table(hcc78.criz.enrich, "hcc78.criz", p_value = 0.01)
all_results <- full_join(all_results, hcc78.criz.enrich.format, by = "Cluster")

h2228.criz.enrich.format <- format_enrichment_table(h2228.criz.enrich, "h2228.criz", p_value = 0.01)
all_results <- full_join(all_results, h2228.criz.enrich.format, by = "Cluster")

ste1.criz.enrich.format <- format_enrichment_table(ste1.criz.enrich, "ste1.criz", p_value = 0.01)
all_results <- full_join(all_results, ste1.criz.enrich.format, by = "Cluster")

pc9.erl.enrich.format <- format_enrichment_table(pc9.erl.enrich, "pc9.erl", p_value = 0.01)
all_results <- full_join(all_results, pc9.erl.enrich.format, by = "Cluster")

hcc4006.erl.enrich.format <- format_enrichment_table(hcc4006.erl.enrich, "hcc4006.erl", p_value = 0.01)
all_results <- full_join(all_results, hcc4006.erl.enrich.format, by = "Cluster")

hcc827.erl.enrich.format <- format_enrichment_table(hcc827.erl.enrich, "hcc827.erl", p_value = 0.01)
all_results <- full_join(all_results, hcc827.erl.enrich.format, by = "Cluster")

h3122.pr.enrich.format <- format_enrichment_table(h3122.pr.enrich, "h3122.pr", p_value = 0.01)
all_results <- full_join(all_results, h3122.pr.enrich.format, by = "Cluster")

pc9.pr.enrich.format <- format_enrichment_table(pc9.pr.enrich, "pc9.pr", p_value = 0.01)
all_results <- full_join(all_results, pc9.pr.enrich.format, by = "Cluster")

h1781.afat.enrich.format <- format_enrichment_table(h1781.afat.enrich, "h1781.afat", p_value = 0.01)
all_results <- full_join(all_results, h1781.afat.enrich.format, by = "Cluster")

h2286.dasat.enrich.format <- format_enrichment_table(h2286.dasat.enrich, "h2286.dasat", p_value = 0.01)
all_results <- full_join(all_results, h2286.dasat.enrich.format, by = "Cluster")

h366.dasat.enrich.format <- format_enrichment_table(h366.dasat.enrich, "h366.dasat", p_value = 0.01)
all_results <- full_join(all_results, h366.dasat.enrich.format, by = "Cluster")

#Add column to results table giving number of drug/cell-line combos where that cluster had a significant p-value
all_results$num_exp <- rowSums(!is.na(all_results[2:13]))

write.table(all_results, file = "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/ClusterEnrichment/enrichment_results_01_new.txt", sep = "\t", row.names = FALSE, quote = FALSE)
```

## Make Cytoscape edge and node files for interesting clusters
```{r Plot Clusters}

source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))

#Load the file with the sites and clusters
CCCN_sites_file <- paste(data_path,"sites_by_cluster.txt", sep="")
CCCN_sites <- read.table(CCCN_sites_file, sep = "\t", stringsAsFactors = F, header=T)

#Make Cytoscape files for interesting clusters
cytoscape_file_path = "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/ClusterEnrichment/ClusterEnrichmentCytoscapeFiles/"

#Drug specific clusters
#Cluster 187.216.82: enriched in both cell lines treated with pr and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "187.216.82"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "187.216.82.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "187.216.82.nodes.txt", sep=""))

#Cluster 254.105.7: enriched in 2 criz cell lines only
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "254.105.7"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "254.105.7.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "254.105.7.nodes.txt", sep=""))

#Cluster 7.7.7: enriched in 2 criz cell lines only
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "7.7.7"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "7.7.7.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "7.7.7.nodes.txt", sep=""))

#Cluster 10.53.10: enriched in all criz cell lines, also enriched in h3122.pr
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "10.53.10"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "10.53.10.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "10.53.10.nodes.txt", sep=""))

#Cell-line specific clusters
#Cluster 108.114.173: enriched in h3122 treated with criz or pr and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "108.114.173"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "108.114.173.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "108.114.173.nodes.txt", sep=""))

#Cluster 339.115.27: enriched in pc9 treated with criz or pr and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "339.115.27"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "339.115.27.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "339.115.27.nodes.txt", sep=""))

#Cluster 111.457.239: enriched in pc9 treated with criz or pr and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "111.457.239"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "111.457.239.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "111.457.239.nodes.txt", sep=""))

#Enriched in almost all experiments ("perturbation-specific")
#Cluster 130.141.111: enriched in almost all drug/cell line combos
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "130.141.111"),]
make.cluster.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "130.141.111.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "130.141.111.nodes.txt", sep=""))

#Make list of unique genes in each cluster and write to a file
genes_file_path <-"/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/ClusterEnrichment/ClusterEnrichmentCytoscapeFiles/GenesInClusters/"
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "187.216.82"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_187.216.82.txt", sep=""))

cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "254.105.7"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_254.105.7.txt", sep=""))

cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "7.7.7"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_7.7.7.txt", sep=""))

cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "10.53.10"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_10.53.10.txt", sep=""))

cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "108.114.173"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_108.114.173.txt", sep=""))

cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "339.115.27"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_339.115.27.txt", sep=""))

cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "111.457.239"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_111.457.239.txt", sep=""))

cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "130.141.111"),]
cluster.cf <- gz.cf[which(gz.cf$id %in% cluster_sites$Site),]
cluster_genes <- unique(cluster.cf$Gene.Name)
write(cluster_genes, file = paste(genes_file_path, "genes_130.141.111.txt", sep=""))
  
```

## Make Cytoscape edge and node files for plotting CFN (only) for interesting clusters
Here we will focus on the clusters that are Crizotinib-specific (enriched in at least 2 crizotinib experiments and no
others) and clusters that are responding to both crizotinib and PR171 (enriched in H3122/PR171 and at least one 
crizotinib experiment and no others). The latter clusters are to investigate the cross-talk between criz and PR171
as these are being considered for combination therapy (PMID: 25175099)
```{r Plot Cluster CFN}

source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))

#Load the file with the sites and clusters
CCCN_sites_file <- paste(data_path,"sites_by_cluster.txt", sep="")
CCCN_sites <- read.table(CCCN_sites_file, sep = "\t", stringsAsFactors = F, header=T)

#Make Cytoscape files for interesting clusters
cytoscape_file_path = "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/ClusterEnrichment/ClusterEnrichmentCytoscapeFiles/CFNCytoscapeFiles/"

#Clusters responding to criz only
#Cluster 7.7.7: enriched in 2 criz cell lines and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "7.7.7"),]
make.cfn.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "7.7.7.cfn.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "7.7.7.cfn.nodes.txt", sep=""))

#Cluster 254.105.7: enriched in 2 criz cell lines and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "254.105.7"),]
make.cfn.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "254.105.7.cfn.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "254.105.7.cfn.nodes.txt", sep=""))

#Clusters responding to crizotinib and PR171
#Cluster 10.53.10: enriched in all criz cell lines, also enriched in h3122.pr and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "10.53.10"),]
make.cfn.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "10.53.10.cfn.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "10.53.10.cfn.nodes.txt", sep=""))

#Cluster 28.53.10: enriched in 3/4 criz cell lines, also enriched in h3122.pr, and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "28.53.10"),]
make.cfn.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "28.53.10.cfn.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "28.53.10.cfn.nodes.txt", sep=""))

#Cluster 108.114.173: enriched in H3122.criz and  H3122.pr, and no others
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "108.114.173"),]
make.cfn.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "108.114.173.cfn.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "108.114.173.cfn.nodes.txt", sep=""))

#Cluster 130.141.111: top enriched cluster for hcc78.criz, ste1.criz, pc9.erl, h1781.afat, h366.dasat
cluster_sites <- CCCN_sites[ which(CCCN_sites$Cluster == "130.141.111"),]
make.cfn.cytoscape.files(cluster_sites$Site, gzallt.network.all, edge_filename = paste(cytoscape_file_path, "130.141.111.cfn.edges.txt", sep=""), node_filename = paste(cytoscape_file_path, "130.141.111.cfn.nodes.txt", sep=""))


```

##Make Heatmaps of Clusters
For clusters of interest, get abundance ratios for all sites for all replicates for all drug/cell-line combos that had a significant corrected p-value for enrichment.
```{r Make Cluster Heatmaps}

source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))

#Standardize the experiment names in the column headings of gz.cf so the labels on the plots will look better
gz.cf.good.col.names <- gz.cf
colnames(gz.cf.good.col.names)

good.col.names <- c("id", "Gene.Name", "Approved.Name", "Hugo.Gene.Family", "HPRD.Function", "nodeType", "Domains", "Compartment", "Compartment.Overview", "Total", "Median", "Max", "No.Samples", "No.Modifications", "ppidegree", "ppibetween", "SEPTM.H3122.Criz.1", "SEPTM.H3122.Criz.2", "SEPTM.H3122.Criz.3", "SEPTM.H3122.PR171.1", "SEPTM.H3122.PR171.2", "SEPTM.H3122.PR171.3", "SEPTM.PC9.Erl.1", "SEPTM.PC9.Erl.2", "SEPTM.PC9.Erl.3", "SEPTM.PC9.PR171.1", "SEPTM.PC9.PR171.2", "SEPTM.PC9.PR171.3", "TC.H1781.Afat.1", "TC.H2228.Criz.1", "TC.H2286.Dasat.1", "TC.H3122.Criz.1", "TC.H3122.Criz.2", "TC.H366.Dasat.1", "TC.HCC4006.Erl.1", "TC.HCC78.Criz.1", "TC.HCC78.Criz.2", "TC.HCC827.Erl.1", "TC.PC9.Erl.1", "TC.PC9.Erl.2", "TC.STE.1.Criz.1", "parent", "Node.ID", "norm.ppibetween", "pepdegree", "pepbetween")  

colnames(gz.cf.good.col.names) <- good.col.names

#Make a list where each element is the names of the replicates of a particular drug/cell-line combo and the
#name of the element is the name of the drug/cell-line combo in the all_results table. This will make it easier to 
#select data for the heatmaps.

experiments <- list(c("SEPTM.H3122.Criz.1", "SEPTM.H3122.Criz.2", "SEPTM.H3122.Criz.3", "TC.H3122.Criz.1", "TC.H3122.Criz.2"), c("TC.HCC78.Criz.1", "TC.HCC78.Criz.2"), c("TC.H2228.Criz.1"), c("TC.STE.1.Criz.1"), c("SEPTM.PC9.Erl.1", "SEPTM.PC9.Erl.2", "SEPTM.PC9.Erl.3", "TC.PC9.Erl.1", "TC.PC9.Erl.2"), c("TC.HCC4006.Erl.1"), c("TC.HCC827.Erl.1"), c("SEPTM.H3122.PR171.1", "SEPTM.H3122.PR171.2", "SEPTM.H3122.PR171.3"), c("SEPTM.PC9.PR171.1", "SEPTM.PC9.PR171.2", "SEPTM.PC9.PR171.3"), c("TC.H1781.Afat.1"), c("TC.H2286.Dasat.1"), c("TC.H366.Dasat.1"))

names(experiments) <- colnames(all_results)[2:13]

heatmap_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/ClusterEnrichment/ClusterHeatmaps/"

#Load the file with the sites and clusters
CCCN_sites_file <- paste(data_path,"sites_by_cluster.txt", sep="")
CCCN_sites <- read.table(CCCN_sites_file, sep = "\t", stringsAsFactors = F, header=T)

#Clusters enriched in Criz only
#Make heatmap input table for cluster "254.105.7"
sig.exp.254.105.7 <- get_sig_experiments("254.105.7", all_results, experiments)
heatmap.data.254.105.7 <- get_cluster_abundances("254.105.7", sig.exp.254.105.7, CCCN_sites, gz.cf.good.col.names)

#Make heatmap for 254.105.7
file.254.105.7 <- paste(heatmap_path, "heatmap.254.105.7.jpeg", sep = "")
make.cluster.heatmap(heatmap.data.254.105.7, file.254.105.7, image_width = 6, image_height = 10, order_cols = TRUE)

#Make heatmap input table for cluster "7.7.7"
sig.exp.7.7.7 <- get_sig_experiments("7.7.7", all_results, experiments)
heatmap.data.7.7.7 <- get_cluster_abundances("7.7.7", sig.exp.7.7.7, CCCN_sites, gz.cf.good.col.names)

#Make heatmap for 7.7.7
file.7.7.7 <- paste(heatmap_path, "heatmap.7.7.7.jpeg", sep = "")
make.cluster.heatmap(heatmap.data.7.7.7, file.7.7.7, image_width = 6, image_height = 10, order_cols = TRUE)

#Clusters enriched in Criz and PR171 experiments
#Make heatmap input table for cluster "10.53.10"
sig.exp.10.53.10 <- get_sig_experiments("10.53.10", all_results, experiments)
heatmap.data.10.53.10 <- get_cluster_abundances("10.53.10", sig.exp.10.53.10, CCCN_sites, gz.cf.good.col.names)

#Make heatmap for 10.53.10
file.10.53.10 <- paste(heatmap_path, "heatmap.10.53.10.jpeg", sep = "")
all.10.53.10 <- make.cluster.heatmap(heatmap.data.10.53.10, file.10.53.10, image_width = 6, image_height = 12, order_cols = TRUE)
write.table(all.10.53.10, file = paste(heatmap_path, "10.53.10-sites.txt", sep=""), sep = "\t", quote = FALSE, col.names=NA)


#Make heatmap input table for cluster "28.53.10"
sig.exp.28.53.10 <- get_sig_experiments("28.53.10", all_results, experiments)
heatmap.data.28.53.10 <- get_cluster_abundances("28.53.10", sig.exp.28.53.10, CCCN_sites, gz.cf.good.col.names)

#Make heatmap for 28.53.10
file.28.53.10 <- paste(heatmap_path, "heatmap.28.53.10.jpeg", sep = "")
make.cluster.heatmap(heatmap.data.28.53.10, file.28.53.10, image_width = 6, image_height = 12, order_cols = TRUE)

#Make heatmap input table for cluster 108.114.173
sig.exp.108.114.173 <- get_sig_experiments("108.114.173", all_results, experiments)
heatmap.data.108.114.173 <- get_cluster_abundances("108.114.173", sig.exp.108.114.173, CCCN_sites, gz.cf.good.col.names)

#Make heatmap for 108.114.173
file.108.114.173 <- paste(heatmap_path, "heatmap.108.114.173.jpeg", sep = "")
make.cluster.heatmap(heatmap.data.108.114.173, file.108.114.173, image_width = 6, image_height = 12, order_cols = TRUE)
```

##Make Heatmaps of Clusters--Part 2
Here, make heatmaps for the most enriched cluster for each drug/cell-line combo. Show all of the replicates for that drug cell-line combo.
```{r Make Cluster Heatmaps2}

source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))

#Standardize the experiment names in the column headings of gz.cf so the labels on the plots will look better
gz.cf.good.col.names <- gz.cf
colnames(gz.cf.good.col.names)

good.col.names <- c("id", "Gene.Name", "Approved.Name", "Hugo.Gene.Family", "HPRD.Function", "nodeType", "Domains", "Compartment", "Compartment.Overview", "Total", "Median", "Max", "No.Samples", "No.Modifications", "ppidegree", "ppibetween", "SEPTM.H3122.Criz.1", "SEPTM.H3122.Criz.2", "SEPTM.H3122.Criz.3", "SEPTM.H3122.PR171.1", "SEPTM.H3122.PR171.2", "SEPTM.H3122.PR171.3", "SEPTM.PC9.Erl.1", "SEPTM.PC9.Erl.2", "SEPTM.PC9.Erl.3", "SEPTM.PC9.PR171.1", "SEPTM.PC9.PR171.2", "SEPTM.PC9.PR171.3", "TC.H1781.Afat.1", "TC.H2228.Criz.1", "TC.H2286.Dasat.1", "TC.H3122.Criz.1", "TC.H3122.Criz.2", "TC.H366.Dasat.1", "TC.HCC4006.Erl.1", "TC.HCC78.Criz.1", "TC.HCC78.Criz.2", "TC.HCC827.Erl.1", "TC.PC9.Erl.1", "TC.PC9.Erl.2", "TC.STE.1.Criz.1", "parent", "Node.ID", "norm.ppibetween", "pepdegree", "pepbetween")  

colnames(gz.cf.good.col.names) <- good.col.names

#Make a list where each element is the names of the replicates of a particular drug/cell-line combo and the
#name of the element is the name of the drug/cell-line combo in the all_results table. This will make it easier to 
#select data for the heatmaps.

experiments <- list(c("SEPTM.H3122.Criz.1", "SEPTM.H3122.Criz.2", "SEPTM.H3122.Criz.3", "TC.H3122.Criz.1", "TC.H3122.Criz.2"), c("TC.HCC78.Criz.1", "TC.HCC78.Criz.2"), c("TC.H2228.Criz.1"), c("TC.STE.1.Criz.1"), c("SEPTM.PC9.Erl.1", "SEPTM.PC9.Erl.2", "SEPTM.PC9.Erl.3", "TC.PC9.Erl.1", "TC.PC9.Erl.2"), c("TC.HCC4006.Erl.1"), c("TC.HCC827.Erl.1"), c("SEPTM.H3122.PR171.1", "SEPTM.H3122.PR171.2", "SEPTM.H3122.PR171.3"), c("SEPTM.PC9.PR171.1", "SEPTM.PC9.PR171.2", "SEPTM.PC9.PR171.3"), c("TC.H1781.Afat.1"), c("TC.H2286.Dasat.1"), c("TC.H366.Dasat.1"))

names(experiments) <- colnames(all_results)[2:13]

heatmap_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/ClusterEnrichment/ClusterHeatmaps/"

#Load the file with the sites and clusters
CCCN_sites_file <- paste(data_path,"sites_by_cluster.txt", sep="")
CCCN_sites <- read.table(CCCN_sites_file, sep = "\t", stringsAsFactors = F, header=T)

#Top cluster for hcc78.criz, ste1.criz, pc9.erl, h1781.afat, h366.dasat: 130.141.111
all.130.141.111 <- make.top.cluster.heatmap(exp = c("ste1.criz","hcc78.criz", "pc9.erl", "h1781.afat", "h366.dasat"), cluster = "130.141.111", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="multiple.130.141.111.heatmap.jpeg", image_width = 7, image_height = 15)
write.table(all.130.141.111, file = paste(heatmap_path, "130.141.111-sites.txt", sep=""), sep = "\t", quote = FALSE, col.names=NA)

#Top cluster for h2228.criz and h2286.dasat: 7.29.7
make.top.cluster.heatmap(exp = c("h2228.criz", "h2286.dasat"), cluster = "7.29.7", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="multiple.7.29.7.heatmap.jpeg", image_width = 6, image_height = 15)

#Top cluster for h3122.criz: 10.53.10
make.top.cluster.heatmap(exp = "h3122.criz", cluster = "10.53.10", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="h3122.criz.10.53.10.heatmap.jpeg", image_width = 6, image_height = 15)

#Top cluster for hcc4006.erl: 38.41.40
make.top.cluster.heatmap(exp = "hcc4006.erl", cluster = "38.41.40", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="hcc4006.erl.38.41.40.heatmap.jpeg", image_width = 6, image_height = 15)

#Top cluster for hcc827.erl: 57.41.40
make.top.cluster.heatmap(exp = "hcc827.erl", cluster = "57.41.40", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="hcc827.erl.57.41.40.heatmap.jpeg", image_width = 6, image_height = 15)

#Three clusters tied for most enriched in h3122.pr
#Top cluster for h3122.pr: 90.28.82
make.top.cluster.heatmap(exp = "h3122.pr", cluster = "90.28.82", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="h3122.pr.90.28.82.heatmap.jpeg", image_width = 6, image_height = 15)

#Top cluster for h3122.pr: 28.53.10
make.top.cluster.heatmap(exp = "h3122.pr", cluster = "28.53.10", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="h3122.pr.28.53.10.heatmap.jpeg", image_width = 6, image_height = 15)

#Top cluster for h3122.pr: 176.206.82
make.top.cluster.heatmap(exp = "h3122.pr", cluster = "176.206.82", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="h3122.pr.176.206.82.heatmap.jpeg", image_width = 6, image_height = 15)

#Top cluster for pc9.pr: 109.115.27
make.top.cluster.heatmap(exp = "pc9.pr", cluster = "109.115.27", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="pc9.pr.109.115.27.heatmap.jpeg", image_width = 6, image_height = 15)

#10.53.10 is enriched for both criz and PR171 experiments. Separate these into separate heatmaps
make.top.cluster.heatmap(exp = c("h3122.criz", "hcc78.criz","h2228.criz",	"ste1.criz"), cluster = "10.53.10", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="criz.10.53.10.heatmap.jpeg", image_width = 6, image_height = 15)

make.top.cluster.heatmap(exp = "h3122.pr", cluster = "10.53.10", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="pr171.10.53.10.heatmap.jpeg", image_width = 4, image_height = 15)

make.top.cluster.heatmap(exp = "h1781.afat", cluster = "10.53.10", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="h1781.afat.10.53.10.heatmap.jpeg", image_width = 4, image_height = 15)

make.top.cluster.heatmap(exp = c("h1781.afat", "ste1.criz"), cluster = "10.53.10", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="h1781.afat.ste1.criz10.53.10.heatmap.jpeg", image_width = 4, image_height = 15)

make.top.cluster.heatmap(exp = c("h3122.criz", "hcc78.criz","h2228.criz"), cluster = "10.53.10", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="criz.no.ste1.10.53.10.heatmap.jpeg", image_width = 6, image_height = 15)

make.top.cluster.heatmap(exp = c("pc9.erl", "hcc827.erl"), cluster = "340.310.275", CCCN_sites, gz.cf.good.col.names, filepath = heatmap_path, filename ="erl.340.310.275.heatmap.jpeg", image_width = 6, image_height = 15)


```
