---
title: "Pathway Network Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load_packages}
library(devtools)
library(RCy3)
library(plyr)
library(dplyr)
library(RColorBrewer)
library(gplots)
library(igraph)
library(knitr)
library("BiocStyle")
options(stringsAsFactors=FALSE)

# Note: Start Cytoscape
# ------------------------------------------------------------------------
cytoscapePing ()
cytoscapeVersionInfo ()
#if (!cytoscapePing()=="You are connected to Cytoscape!") {
#     print("Turn on Cytoscape to load New_RCy3_Functions.R")}

```

```{r load data objects and functions}
data_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/TenPTMAnalysis/TenCellLineNetwork-Rfiles2/Rfiles/"
code_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/PTMs-to-CCCN-and-CFN/"
load(file=paste(data_path, "KGFunDataObjects-3.RData", sep=""))
load(file=paste(data_path, "LC_TMT_Nets.RData", sep=""))
load(file=paste(data_path, "TenCell-TKI.RData", sep=""))
load(file=paste(data_path, "GZ_PPI_Networks2.RData", sep="")) #has gz.cf w/12461 rows and gz.cf.pruned w/9701
load(file=paste(data_path, "LD_NewCFNCCCN_Networks.RData", sep=""))
load(file=paste(data_path,"drug_effects.RData", sep=""))
load(file=paste(data_path,"BioPlanetNetworks.RData", sep=""))
	source(paste(code_path, "Data_Input_Formatting.R", sep=""))
	#source(paste(code_path, "Dissimilarity_Calculations.R", sep=""))
	source(paste(code_path, "Generate_CCCN_CFN.R", sep=""))
  source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))

```

```{r plot full cfn and cccn}
#Plot the full cfn and cccn. Once this is done in a Cytoscape session, it will not be necessary to run all.ratio.styles() on each smaller subnetwork

full_network <- graph.cfn.cccn.title(gzallt.physical.network, ld=FALSE, gz=TRUE, only.cfn=FALSE, pruned=FALSE, custom.title = "CFN plus CCCN, Physical Interactions")
all.ratio.styles()

```
## EGFR

The goal here is to make a version of the pathway network where the interacting pathways have strong cluster evidence and little overlap of genes. Then find all pairs of pathways in that network where at least one of the pathways contains EGFR.

```{r EGFR pathway networks}

#Make a version of the pathway network where the interacting pathways have strong cluster evidence and little overlap of genes.
selected.pathway.edges <- big.path.net[big.path.net$Weight.clust > 0.8 & big.path.net$Weight.bp < 0.001,]
nrow(selected.pathway.edges) #251
num_nodes <- length(unique(c(selected.pathway.edges$source, selected.pathway.edges$target)))

#Find names of all pathways in Bioplanet that contain EGFR. The data object 'bioplanet' is a list, where the name of the list element is the name of a Bioplanet pathway and each element is a character vector of the genes in that pathway
egfr_pathways <- names(bioplanet)[sapply(1:length(bioplanet),function(x){"EGFR" %in% bioplanet[[x]]})]
length(egfr_pathways) #83

#Now select the rows from the pathway interaction network where either of the two pathways contains EGFR
selected.pathways.egfr <- selected.pathway.edges[which((selected.pathway.edges$source %in% egfr_pathways) | (selected.pathway.edges$target %in% egfr_pathways)),]
nrow(selected.pathways.egfr) #29

#Find the number of unique pathways included in those 29 pathway pairs
unique.paths <- union(selected.pathways.egfr$source, selected.pathways.egfr$target)
length(unique.paths) #29--I think it is a coincidence that there are 29 pairs and 29 unique pathways

#Find out how many of the 29 unique pathways contain EGFR
unique.pathway.list <- bioplanet[unique.paths]
unique.pathways.egfr <- sapply(1:length(unique.pathway.list), function(x) {"EGFR" %in% unique.pathway.list[[x]]})
sum(unique.pathways.egfr) #13

#Make list of the 13 EGFR containing pathways in the pathway crosstalk network
unique.pathways.egfr.list <- unique.pathway.list[unique.pathways.egfr]

#For each pair of pathways, find the edges from the cfn that connect a gene from pathway 1 with a gene from pathway 2. Use the filter.edges.between function and use mapply to apply this to all pathway pairs in selected.pathways.egfr. The output is a list of dataframes with each list element being the results of a pathway pair.

pathway.crosstalk.egfr <- mapply(function(x,y) {filter.edges.between(bioplanet[[x]], bioplanet[[y]], edge.file=gzalltgene.physical.cfn.merged)}, x = selected.pathways.egfr$source, y= selected.pathways.egfr$target, SIMPLIFY = FALSE)

#Change the names of the list elements to be Pathway A*Pathway B
names(pathway.crosstalk.egfr) <- paste(selected.pathways.egfr$source, selected.pathways.egfr$target, sep = "*")

#Next task...for each list of interactions, find those where one or both genes had a PTM with a signficant change in erlotinib

#Find genes that had at least one site where that site was changed at least 2.25-fold in at least two PC9 erlotinib experiments. NOTE: Ratios in gz.cf are in log2.
#Remove gene lines from gz.cf, and then make a smaller version of gz.cf with only the site, gene, and PC9 erlotinib columns
gz.cf.erl <- gz.cf[which (gz.cf$Node.ID == "peptide"), ]
gz.cf.erl <- gz.cf.erl[c("id", "Gene.Name", "PC9SEPTM.E1.ratio", "PC9SEPTM.E2.ratio", "PC9SEPTM.E3.ratio", "PC9_Erlotinib.1Ratio", "PC9_ErlotinibRatio")]
gz.cf.erl$count_up <- rowSums(gz.cf.erl[3:7] > log2(2.25))
gz.cf.erl$count_down <- rowSums(gz.cf.erl[3:7] < -log2(2.25))
gz.cf.erl.keep <- gz.cf.erl[which((gz.cf.erl$count_down > 1) | (gz.cf.erl$count_up > 1)),]

#Now get the unique gene names that meet the condition
gz.cf.erl.keep.genes <- unique(gz.cf.erl.keep$Gene.Name) #383 genes

#Select the rows from each set of cross-pathway interactions in pathway.crosstalk.egfr where at least one gene meets the condition. Test this first on just the first set of interactions
test <- pathway.crosstalk.egfr[[1]]
test2 <- test[ which((test$source %in% gz.cf.erl.keep.genes) | (test$target %in% gz.cf.erl.keep.genes)),] #101 rows

#Now find cases where both genes in the interaction meet the condition
test3 <- test[ which((test$source %in% gz.cf.erl.keep.genes) & (test$target %in% gz.cf.erl.keep.genes)),] #35 rows

#Now apply to all 29 pathway pairs in pathway.crosstalk.egfr. This selects the cross pathway interactions where at least one of the two interacting genes is at least 2.25-fold up or 2.25-fold down in at least two experiments
pathway.crosstalk.egfr.changed.genes <- lapply(1:length(pathway.crosstalk.egfr),function(x) {pathway.crosstalk.egfr[[x]][ which((pathway.crosstalk.egfr[[x]]$source %in% gz.cf.erl.keep.genes) | (pathway.crosstalk.egfr[[x]]$target %in% gz.cf.erl.keep.genes)),]})

#Name the sets of interaction using the pair of pathways they come from
names(pathway.crosstalk.egfr.changed.genes) <- names(pathway.crosstalk.egfr)

#Number of interactions for each pathway pair where at least one gene meets the condition
rows.changed.genes <- sapply(1:length(pathway.crosstalk.egfr.changed.genes),function(x) {nrow(pathway.crosstalk.egfr.changed.genes[[x]])})

#[1] 101   9  25  10  12  36  43  12  24  44  28  44  14  12  11   4  15  25  30  16  22  14   7  11
#[25]   2   0   8   2  15

#For all 29 pathway pairs in pathway.crosstalk.egfr, this selects the cross pathway interactions where BOTH of the interacting genes are at least 2.25-fold up or 2.25-fold down in at least two experiments
pathway.crosstalk.egfr.changed.genes.both <- lapply(1:length(pathway.crosstalk.egfr),function(x) {pathway.crosstalk.egfr[[x]][ which((pathway.crosstalk.egfr[[x]]$source %in% gz.cf.erl.keep.genes) & (pathway.crosstalk.egfr[[x]]$target %in% gz.cf.erl.keep.genes)),]})

#Name the sets of interaction using the pair of pathways they come from
names(pathway.crosstalk.egfr.changed.genes.both) <- names(pathway.crosstalk.egfr)

#Number of interactions for each pathway pair where both genes meet the condition
rows.changed.genes.both <- sapply(1:length(pathway.crosstalk.egfr.changed.genes.both),function(x) {nrow(pathway.crosstalk.egfr.changed.genes.both[[x]])})

#[1] 35  6  5  4  6 10 12  5 13 15  6 11  4  6  3  2  8  8 10  7  7  4  4  7  0  0  2  0  4

```

```{r Plot EGFR pathway networks}
#Make Cytoscape networks containing CFN and CCCN for each of the pairs of pathways in pathway.crosstalk.egfr.changed.genes.both. These are saved in Cytoscape session pathway_crosstalk_networks_both_changed2.cys. Note: if networks are being If the networks are being created in a Cytoscape session where the full cfn/cccn with all styles has already been created, then the functions specifying the node and edge properties setNodeMapping and setCorrEdgeAppearance can be commented out. This will make the network creation _much_ faster.

source(paste(code_path, "Generate_CCCN_CFN.R", sep=""))

graph.crosstalk.network <- function(edgefile, my.title) {
  if (nrow(edgefile) > 0) {
    graph.cfn.cccn.title(edgefile, custom.title = my.title)
  }
}

crosstalk.networks.all <- lapply(1:length(pathway.crosstalk.egfr.changed.genes.both), function(x) {graph.crosstalk.network(pathway.crosstalk.egfr.changed.genes.both[[x]], names(pathway.crosstalk.egfr.changed.genes.both[x]))})

#Make Cytoscape networks containing CFN and CCCN for each of the pairs of pathways in pathway.crosstalk.egfr.changed.genes. These are saved in Cytoscape session pathway_crosstalk_networks_one_changed2.cys.

crosstalk.networks.one.changed <- lapply(1:length(pathway.crosstalk.egfr.changed.genes), function(x) {graph.crosstalk.network(pathway.crosstalk.egfr.changed.genes[[x]], names(pathway.crosstalk.egfr.changed.genes[x]))})

```



## EGFR Network Statistics
1. How many of the genes affected by erlotinib are found in the pairs of pathways from the pathways interaction network where at least one of the pathways contains EGFR? Is this number higher than you would expect by chance?
```{r EGFR pathway network stats}
#How many of the genes with at least one site changed in at least two PC9/Erlotinib experiments are found in the 29 unique pathways in selected.pathways.egfr
selected.genes.all <- unique(unlist(unique.pathway.list)) #3741 genes total in these 29 pathways
num.erl.in.paths <- sum(gz.cf.erl.keep.genes %in% selected.genes.all) #188 out of 383

#How interesting is it that 188 out of 383 PC9/erlotinib changed genes are found in the 29 pathways?
gz.cf.genes.all <- unique(gz.cf$Gene.Name) 
length(gz.cf.genes.all) #3246
sum(selected.genes.all %in% gz.cf.genes.all) #1145 of 3741 genes in the 29 paths found in gz.cf

#Proportion of total genes in gz.cf that are in the selected 29 pathways is 1145/3246 = 0.35. 0.35 * 383 = 134.05; so on average you would expect ~134 out of 383 genes randomly selected from gz.cf.genes.all to be in the selected 29 pathways. How unusual is it to get 188? We could do a fisher test:
num.erl.not.in.paths <- length(gz.cf.erl.keep.genes) - num.erl.in.paths
num.not.erl.in.paths <- sum(selected.genes.all %in% gz.cf.genes.all) - num.erl.in.paths
num.not.erl.not.in.paths <- length(gz.cf.genes.all) - sum(selected.genes.all %in% gz.cf.genes.all) - num.erl.not.in.paths

fisher.input <- matrix(c(num.erl.in.paths, num.erl.not.in.paths, num.not.erl.in.paths, num.not.erl.not.in.paths), nrow = 2)
fisher.result <- fisher.test(fisher.input, alternative = "greater") # p = 2.32e-09

#Another check: select 383 genes at random 10,000 times and see how many are in the selected pathways in each case
genes.in.paths.random <- replicate(10000, sum(sample(gz.cf.genes.all, size = 383) %in% selected.genes.all))
min(genes.in.paths.random) #103
max(genes.in.paths.random) #168
mean(genes.in.paths.random) #135.0196
#We observed 188 genes which is higher than the max in our random sample. So, the probability of getting 188 is < 1/10,000 (< 1e-04). 

#Can also try with 100,000 repetitions
genes.in.paths.random2 <- replicate(100000, sum(sample(gz.cf.genes.all, size = 383) %in% selected.genes.all))
min(genes.in.paths.random2) #101
max(genes.in.paths.random2) #171
mean(genes.in.paths.random2) #135.094
sum(genes.in.paths.random2 > 187) #0
#In this larger random sample, there were still no results that were 188 or more, so the probability of getting 188 or more is < 1/100,000 or 1e-05.

#What about just the 13 pathways that contain EGFR?
selected.genes.egfr <- unique(unlist(unique.pathways.egfr.list)) #2120 genes total in these 13 pathways
sum(selected.genes.egfr %in% gz.cf.genes.all) #726 of these genes in gz.cf
num.erl.in.egfr.pathways <- sum(gz.cf.erl.keep.genes %in% selected.genes.egfr) #131 out of 383 erlotinib-affected genes

#Is having 131/383 erlotinib affected genes in the EGFR pathways significant? Expect 726/3246 * 383 = 85.66
genes.in.paths.random4 <- replicate(100000, sum(sample(gz.cf.genes.all, size = 383) %in% selected.genes.egfr))
min(genes.in.paths.random4) #53
max(genes.in.paths.random4) #126
mean(genes.in.paths.random4) #31.97
sum(genes.in.paths.random4 > 130) #0

#There were 0 results that were 131 or more, so the probability of getting 131 or more is  < 1/100,000 or 1e-05. 

#What about the 16 selected pathways that do not contain EGFR?
unique.pathways.not.egfr.list <- unique.pathway.list[!unique.pathways.egfr] #List of 16 selected pathways that do not have EGFR
selected.genes.not.egfr <- unique(unlist(unique.pathways.not.egfr.list)) #2169 genes in these 16 pathways
sum(selected.genes.not.egfr %in% gz.cf.genes.all) #690 genes in gz.cf
num.erl.in.not.egfr.pathways <- sum(gz.cf.erl.keep.genes %in% selected.genes.not.egfr) #115 erl-changed genes in non-EGFR paths

#There are 3246 total genes in gz.cf; 690/3246 = 0.2125 are in the selected non-EGFR pathways. If you selected 383 genes at random from gz.cf, you would expect 0.213 * 388 = 81.41 to be in the selected non-EGFR pathways. We observed 115. Is this significant?
genes.in.paths.random3 <- replicate(100000, sum(sample(gz.cf.genes.all, size = 383) %in% selected.genes.not.egfr))
min(genes.in.paths.random3) #52
max(genes.in.paths.random3) #117
mean(genes.in.paths.random3) #81.39
sum(genes.in.paths.random3 > 114) #1

#So the probability of getting at least 115 is 1/100000 = 1e-05.

#How many of the erl-changed genes in the EGFR subset are also in the non-EGFR subset?
egfr.path.genes <- gz.cf.erl.keep.genes[gz.cf.erl.keep.genes %in% selected.genes.egfr]
not.egfr.path.genes <- gz.cf.erl.keep.genes[gz.cf.erl.keep.genes %in% selected.genes.not.egfr]
sum(egfr.path.genes %in% not.egfr.path.genes) #58 erl-changed genes are found in both EGFR-containing and non-EGFR containing selected pathways

#There are quite a few (58/188) erl-changed genes in the interacting non-EGFR pathways that are also in the EGFR pathways. This might suggest that non-EGFR containing pathways that interact with EGFR pathways are more likely to have genes in common with EGFR pathways.

#Bottom line: Erlotinib-affected genes are more likely than a random set of genes from gz.cf to be in the selected pathways overall, the subset of selected pathways that contain EGFR, and in the subset of pathways that do not contain EGFR. 

#But maybe just being in a Bioplanet pathway makes a gene more likely to be erlotinib affected? What if we selected other random subsets of 29 Bioplanet pathways?

#First, how many genes in gz.cf are in at least one Bioplanet pathway?
genes_bioplanet <- unique(unlist(bioplanet))
num_genes_bioplanet <- length(unique(unlist(bioplanet))) #9818 genes in bioplanet
bioplanet_genes_in_gz.cf <- gz.cf.genes.all[gz.cf.genes.all %in% genes_bioplanet]
num_bioplanet_genes_in_gz.cf <- length(bioplanet_genes_in_gz.cf) #2120
sum(selected.genes.egfr %in% bioplanet_genes_in_gz.cf) #726
#This is a weird coincidence: The number of genes in the 13 EGFR pathways in Bioplanet (2120) is equal to the number of genes in all Bioplanet pathways that are in gz.cf (2120). However, these two gene lists are not the same. There are only 726 genes from the EGFR Bioplanet pathways that are in gz.cf. 

sample.bioplanet <- function(num_pathways= 29) {
  pathways <- sample(bioplanet, size = num_pathways)
  genes <- unique(unlist(pathways))
  erl_changed <- sum(gz.cf.erl.keep.genes %in% genes)
  return(erl_changed)
    
}

erl.changed.random.paths <- replicate(100000, sample.bioplanet(num_pathways = 29))
min(erl.changed.random.paths) #11
max(erl.changed.random.paths) #156
mean(erl.changed.random.paths) #59.45
sum(erl.changed.random.paths > 187) #0

#With a random selection of 29 Bioplanet pathways, the chances are less than 1e-05 that there will be at least 188 erlotinib changed genes. However, our selected 29 pathways included 13 pathways that contain EGFR and would be expected to be enriched for erlotinib changed genes. Try the random sample using the numbers for the non-EGFR containing pathways--16 pathways and 115 erlotinib-changed genes.

erl.changed.random.paths2 <- replicate(100000, sample.bioplanet(num_pathways = 16))
min(erl.changed.random.paths2) #2
max(erl.changed.random.paths2) #135
mean(erl.changed.random.paths2) #37.75
sum(erl.changed.random.paths2 > 114) #58

#With a random selection of 16 Bioplanet pathways, the chances are 58/100000 = 5.8e-04 that there will be at least 115 erlotinib changed genes. 

#First test: Are erlotinib-affected genes more likely than a random set of genes from gz.cf to be in the selected pathways? Yes. #Second test: Do the selected pathways include an unusually high number of erlotinib-affected genes compared to a randomly selected set of pathways from Bioplanet. Yes (True for both the overall 29 selected pathways (with 188 erlotinib changed genes) and for the 16 selected pathways that do not contain EGFR (with 115 erlotinib changed genes)).

#Next up: how many unique genes are in the interaction networks? In how many networks does each gene appear? How many unique edges are there? In how many networks does each edge appear?

```

#Comparison of EGFR Cross Pathway Interactions
From browsing through the networks, it is apparent that many of the cross-pathway interactions networks for different pairs of pathways have genes and edges in common. How many unique genes are in the interaction networks? In how many networks does each gene appear? How many unique edges are there? In how many networks does each edge appear?

```{r EGFR pathway network commonalities}
#How many total edges are there in the networks where at least one interactor has an erl changed site?
sum(rows.changed.genes) #596 Total number of edges in all networks including duplicates

#Combine the edges from all networks into a single dataframe and tally the number of times each source/target pair appears
all.rows <- bind_rows(pathway.crosstalk.egfr.changed.genes, .id = "column_label")
edge.tally <- plyr::count(all.rows, var = c("source", "target")) #318 rows
#Problem: this tallies "source = a, target = b" separately from "source = b, target = a"
#Instead try this: take just the source and target columns from all rows, sort each row alphabetically, then do the plyr::count step.
all.rows.sorted <- all.rows[c("source", "target")]
all.rows.sorted <- as.data.frame(t(apply(all.rows.sorted,1,function(x) sort(x))))
colnames(all.rows.sorted) <- c("gene1", "gene2")
edge.tally.sorted <- plyr::count(all.rows.sorted, var = c("gene1", "gene2")) #315 rows (315 unique edges)

#Sort edge tally dataframe in descending order by frequency
edge.tally.sorted <- edge.tally.sorted[order(edge.tally.sorted$freq, decreasing = TRUE),]

#Same thing for the networks where both interactors have an erl changed site
#How many total edges are there in the networks where both interactors have an erl changed site?
sum(rows.changed.genes.both) #204 (includes duplicates)

#Combine the edges from all networks into a single dataframe and tally the number of times each source/target pair appears
all.rows.both <- bind_rows(pathway.crosstalk.egfr.changed.genes.both, .id = "column_label")
all.rows.both.sorted <- all.rows.both[c("source", "target")]
all.rows.both.sorted <- as.data.frame(t(apply(all.rows.both.sorted,1,function(x) sort(x))))
colnames(all.rows.both.sorted) <- c("gene1", "gene2")
edge.tally.both.sorted <- plyr::count(all.rows.both.sorted, var = c("gene1", "gene2")) #101 rows (101 unique edges)

#Sort edge tally dataframe in descending order by frequency
edge.tally.both.sorted <- edge.tally.both.sorted[order(edge.tally.both.sorted$freq, decreasing = TRUE),]


```


