---
title: "RCy3 Plotting of CCCN and CFN "
output: github_document
Author: "Mark Grimes
        University of Montana"
---
Note: 'biocLite' is deprecated.
Use 'BiocManager::install' instead.
---
# Lung cancer plus ten cell line data
# August 12, 2019
# Mark Grimes
---
# Note: Cytoscape 3.7.1 or greater is required. Start Cytoscape and make sure cyREST is activated before running this script.
# This loads MGs packages and functions and lists the data objects from the new data:
```{r}
# # ------------------------------------------------------------------------
# To UpDATE
# source("http://www.bioconductor.org/biocLite.R")
# biocLite("RCy3")
# biocLite("BiocStyle")
# Try the latest version of RCy3 by running:
    # install.packages("BiocManager")
    #   BiocManager::install("RCy3")
library(devtools)
library(RCy3)
library(plyr)
library(dplyr)
library(RColorBrewer)
library(gplots)
library(igraph)
library(knitr)
library("BiocStyle")
options(stringsAsFactors=FALSE)
#
# There are several resources available:
browseVignettes('RCy3')
# https://github.com/cytoscape/RCy3/wiki/Upgrading-Existing-Scripts
# 
#MAY 19th make a change
# Note: Start Cytoscape
# ------------------------------------------------------------------------
cytoscapePing ()
cytoscapeVersionInfo ()

```
---

---
```{r load data objects and functions}
 options(stringsAsFactors=FALSE)
options(stringsAsFactors=FALSE)
data_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/TenPTMAnalysis/TenCellLineNetwork-Rfiles2/Rfiles/"
code_path <- "/Users/karenross/Documents/Bioinformatics/PIR/GrimesGroupCollab/PTMs-to-CCCN-and-CFN/"
load(file=paste(data_path, "KGFunDataObjects.RData", sep=""))
load(file=paste(data_path, "LC_TMT_Nets.RData", sep=""))
load(file=paste(data_path, "TenCell.RData", sep=""))
load(file=paste(data_path, "GZ_PPI_Networks2.RData", sep=""))
load(file=paste(data_path, "LD_NewCFNCCCN_Networks.RData", sep=""))
load(file=paste(data_path,"drug_effects.RData", sep=""))
	source(paste(code_path, "Data_Input_Formatting.R", sep=""))
	source(paste(code_path, "Dissimilarity_Calculations.R", sep=""))
	source(paste(code_path, "Generate_CCCN_CFN.R", sep=""))
    source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))
if (!cytoscapePing()=="You are connected to Cytoscape!") {
     print("Turn on Cytoscape to load New_RCy3_Functions.R")}

```

#This chunk selects sites from an experiment with absolute fold-change greater than a specified value. Then it computes the shortest paths in the CFN from the selected sites to a specified target (e.g, the drug target). Then it computes and draws the union and intersection of the shortest paths networks and draws the networks. PC9/erlotinib is used as an example.  
```{r shortest paths to target for PC9/erlotinib-independent experiments method}
#There are 5 PC9/erlotinib experiments ("PC9SEPTM.E1.ratio", "PC9SEPTM.E2.ratio", "PC9SEPTM.E3.ratio", "PC9_Erlotinib.1Ratio", "PC9_ErlotinibRatio"). For each experiment select sites that have abs fold-change > 2.25-fold. Then find the shortest paths to EGFR.

selected_sites_S1 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E1.ratio", min_value = 2.25)
paths_S1 <- shortest.paths.to.target(selected_sites_S1, target = "EGFR")

selected_sites_S2 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E2.ratio", min_value = 2.25)
paths_S2 <- shortest.paths.to.target(selected_sites_S2, target = "EGFR")

selected_sites_S3 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E3.ratio", min_value = 2.25)
paths_S3 <- shortest.paths.to.target(selected_sites_S3, target = "EGFR")

selected_sites_T1 <- select.sites.w.min.value(gz.cf, "PC9_Erlotinib.1Ratio", min_value = 2.25)
paths_T1 <- shortest.paths.to.target(selected_sites_T1, target = "EGFR")

selected_sites_T2 <- select.sites.w.min.value(gz.cf, "PC9_ErlotinibRatio", min_value = 2.25)
paths_T2 <- shortest.paths.to.target(selected_sites_T2, target = "EGFR")

#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
S_union <- my.union(paths_S1, paths_S2, paths_S3)
union_network <- graph.cfn.cccn (S_union, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
S_intersect <- my.intersect(paths_S1, paths_S2, paths_S3)
intersect_network <- graph.cfn.cccn (S_intersect, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

```  

# This chunk selects sites for a particular cell line/drug combo that meet criteria for minimum number of observations, minimum absolute value of mean for the ratio, and maximun coefficient of variation for the ratio. Then it computes the shortest paths in the CFN from the selected sites to a specified target (e.g, the drug target) and draws the network. PC9/erlotinib is used as an example.  

```{r shortest paths to target for PC9/erlotinib-mean/CV method}
#There are 5 PC9/erlotinib experiments (3 from SEPTM and 2 from TenCellLines). Select sites that (i) have observed values in at least two experiments; (ii) have mean change of at least 2.25-fold; (iii) have a "small" standard deviation. Calculate the coefficient of variation for log-transformed data (https://en.wikipedia.org/wiki/Coefficient_of_variation). Select sites with CV<=1.

all_cols <- colnames(gz.cf)
all_cols

#Make a dataframe with just the following columns from gz.cf: id, Gene.Name and the 5 PC9/Erlotinib data columns
desired_cols <- c("id", "Gene.Name", "PC9SEPTM.E1.ratio", "PC9SEPTM.E2.ratio", "PC9SEPTM.E3.ratio", "PC9_Erlotinib.1Ratio", "PC9_ErlotinibRatio")

#Select the rows that have at least 2 (non-NA) observations
gz_pc9_erl.cf <- gz.cf[desired_cols]
gz_pc9_erl_keep.cf <- select.sites.w.enough.obs(gz_pc9_erl.cf, num_rep = 5, min_obs = 2)
nrow(gz_pc9_erl_keep.cf)

#Calculate the mean and keep only those rows with abs(mean) > log2(2.25)
gz_pc9_erl_keep2.cf <- select.sites.w.min.mean(gz_pc9_erl_keep.cf, first_rep = 3, num_rep = 5, min_mean = 2.25)
nrow(gz_pc9_erl_keep2.cf)

#Calculate the log-transformed coefficient of variation for each row and keep only rows with CV <=1
gz_pc9_erl_keep2.cf <- select.sites.w.max.cv(gz_pc9_erl_keep2.cf, first_rep = 3, num_rep =5, max_cv = 1)
nrow(gz_pc9_erl_keep2.cf)

#Now compute the shortest paths network for this set of sites and make Cytoscape graph.
gz_pc9_erl_keep2_paths <- shortest.paths.to.target(gz_pc9_erl_keep2.cf, target = "EGFR")
nrow(gz_pc9_erl_keep2_paths)
changed_genes_network <- graph.cfn.cccn (gz_pc9_erl_keep2_paths, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()


```  


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

