---
title: "RCy3 Plotting of CCCN and CFN "
output: github_document
Author: "Mark Grimes
        University of Montana"
---
Note: 'biocLite' is deprecated.
Use 'BiocManager::install' instead.
---
# Lung cancer plus ten cell line data
# August 12, 2019
# Mark Grimes
---
# Note: Cytoscape 3.7.1 or greater is required. Start Cytoscape and make sure cyREST is activated before running this script.
# This loads MGs packages and functions and lists the data objects from the new data:
```{r}
# # ------------------------------------------------------------------------
# To UpDATE
# source("http://www.bioconductor.org/biocLite.R")
# biocLite("RCy3")
# biocLite("BiocStyle")
# Try the latest version of RCy3 by running:
    # install.packages("BiocManager")
    #   BiocManager::install("RCy3")
library(devtools)
library(RCy3)
library(plyr)
library(dplyr)
library(RColorBrewer)
library(gplots)
library(igraph)
library(knitr)
library("BiocStyle")
options(stringsAsFactors=FALSE)
#
# There are several resources available:
browseVignettes('RCy3')
# https://github.com/cytoscape/RCy3/wiki/Upgrading-Existing-Scripts
# 
#MAY 19th make a change
# Note: Start Cytoscape
# ------------------------------------------------------------------------
cytoscapePing ()
cytoscapeVersionInfo ()

```
---

---
```{r load data objects and functions}
 options(stringsAsFactors=FALSE)
options(stringsAsFactors=FALSE)
data_path <- "C:/Users/yulin/Desktop/Multi-PTM Analysis-Summer Students/RDataFiles/"
code_path <- "C:/Users/yulin/Documents/Bioinformatics/SUMMER_GIT/PTMs-to-CCCN-and-CFN5_19/"
load(file=paste(data_path, "KGFunDataObjects.RData", sep=""))
load(file=paste(data_path, "LC_TMT_Nets.RData", sep=""))
load(file=paste(data_path, "TenCell.RData", sep=""))
load(file=paste(data_path, "GZ_PPI_Networks2.RData", sep=""))
load(file=paste(data_path, "LD_NewCFNCCCN_Networks.RData", sep=""))
load(file=paste(data_path,"drug_effects.RData", sep=""))
	source(paste(code_path, "Data_Input_Formatting.R", sep=""))
	source(paste(code_path, "Dissimilarity_Calculations.R", sep=""))
	source(paste(code_path, "Generate_CCCN_CFN.R", sep=""))
    source(paste(code_path, "CFN_CCCN_Analysis.R", sep=""))
if (!cytoscapePing()=="You are connected to Cytoscape!") {
     print("Turn on Cytoscape to load New_RCy3_Functions.R")}

```

#This chunk selects sites from an experiment with absolute fold-change greater than a specified value. Then it computes the shortest paths in the CFN from the selected sites to a specified target (e.g, the drug target). Then it computes and draws the union and intersection of the shortest paths networks and draws the networks. PC9/erlotinib is used as an example.  
```{r shortest paths to target for PC9/erlotinib-independent experiments method}
#There are 5 PC9/erlotinib experiments ("PC9SEPTM.E1.ratio", "PC9SEPTM.E2.ratio", "PC9SEPTM.E3.ratio", "PC9_Erlotinib.1Ratio", "PC9_ErlotinibRatio"). For each experiment select sites that have abs fold-change > 2.25-fold. Then find the shortest paths to EGFR.

selected_sites_S1 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E1.ratio", min_value = 2.25)
paths_S1 <- shortest.paths.to.target(selected_sites_S1, target = "EGFR")

selected_sites_S2 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E2.ratio", min_value = 2.25)
paths_S2 <- shortest.paths.to.target(selected_sites_S2, target = "EGFR")

selected_sites_S3 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E3.ratio", min_value = 2.25)
paths_S3 <- shortest.paths.to.target(selected_sites_S3, target = "EGFR")

selected_sites_T1 <- select.sites.w.min.value(gz.cf, "PC9_Erlotinib.1Ratio", min_value = 2.25)
paths_T1 <- shortest.paths.to.target(selected_sites_T1, target = "EGFR")

selected_sites_T2 <- select.sites.w.min.value(gz.cf, "PC9_ErlotinibRatio", min_value = 2.25)
paths_T2 <- shortest.paths.to.target(selected_sites_T2, target = "EGFR")

#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
S_union <- my.union(paths_S1, paths_S2, paths_S3)
union_network <- graph.cfn.cccn (S_union, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
S_intersect <- my.intersect(paths_S1, paths_S2, paths_S3)
intersect_network <- graph.cfn.cccn (S_intersect, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

```  
# An updated full version of all paths for each replicates
# ss = selected sites

```{r}
##### Crizotinib
# cell line = H3122, ExpSet = SEPTM, Drug = Crizotinib, rep = 3

ss1 <- select.sites.w.min.value(gz.cf, "H3122SEPTM.C1.ratio", min_value = 2.25)
paths_1 <- shortest.paths.to.target(ss1, target = "ALK")

ss2 <- select.sites.w.min.value(gz.cf, "H3122SEPTM.C2.ratio", min_value = 2.25)
paths_2 <- shortest.paths.to.target(ss2, target = "ALK")

ss3 <- select.sites.w.min.value(gz.cf, "H3122SEPTM.C3.ratio", min_value = 2.25)
paths_3 <- shortest.paths.to.target(ss3, target = "ALK")

#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_1 <- my.union(paths_1, paths_2, paths_3)
union_network <- graph.cfn.cccn (U_1, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_1 <- my.intersect(paths_1, paths_2, paths_3)
intersect_network <- graph.cfn.cccn (I_1, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

###
# cell line = H3122, ExpSet = TenCell, Drug = Crizotinib, rep = 2

ss4 <- select.sites.w.min.value(gz.cf, "H3122_Crizotinib.1Ratio", min_value = 2.25)
paths_4 <- shortest.paths.to.target(ss4, target = "ALK")

ss5 <- select.sites.w.min.value(gz.cf, "H3122CrizotinibRatio", min_value = 2.25)
paths_5 <- shortest.paths.to.target(ss5, target = "ALK")


###
# cell line = HCC78, ExpSet = TenCell, Drug = Crizotinib, rep = 2

ss6 <- select.sites.w.min.value(gz.cf, "HCC78_Crizotinib.1Ratio", min_value = 2.25)
paths_HC_T_Cri_rep1 <- shortest.paths.to.target(ss6, target = "ALK")

ss7 <- select.sites.w.min.value(gz.cf, "HCC78_CrizotinibRatio", min_value = 2.25)
paths_7 <- shortest.paths.to.target(ss7, target = "ALK")

###
# cell line = STE.1, ExpSet = TenCell, Drug = Crizotinib, rep = 1

ss8 <- select.sites.w.min.value(gz.cf, "STE.1_CrizotinibRatio", min_value = 2.25)
paths_8 <- shortest.paths.to.target(ss8, target = "ALK")

# cell line = H2228, ExpSet = TenCell, Drug = Crizotinib, rep = 1

ss9 <- select.sites.w.min.value(gz.cf, "H2228CrizotinibRatio", min_value = 2.25)
paths_9 <- shortest.paths.to.target(ss9, target = "ALK")


##### Erlotinib
# cell line = PC9, ExpSet = SEPTM, Drug = Erlotinib, rep = 3

ss10 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E1.ratio", min_value = 2.25)
paths_10 <- shortest.paths.to.target(ss10, target = "EGFR")

ss11 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E2.ratio", min_value = 2.25)
paths_11 <- shortest.paths.to.target(ss11, target = "EGFR")

ss12 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.E3.ratio", min_value = 2.25)
paths_12 <- shortest.paths.to.target(ss12, target = "EGFR")

# cell line = PC9, ExpSet = TenCell, Drug = Erlotinib, rep = 2

ss13 <- select.sites.w.min.value(gz.cf, "PC9_Erlotinib.1Ratio", min_value = 2.25)
paths_13 <- shortest.paths.to.target(ss13, target = "EGFR")

ss14 <- select.sites.w.min.value(gz.cf, "PC9_ErlotinibRatio", min_value = 2.25)
paths_14 <- shortest.paths.to.target(ss14, target = "EGFR")

# cell line = HCC4006, ExpSet = TenCell, Drug = Erlotinib, rep = 1

ss15 <- select.sites.w.min.value(gz.cf, "HCC4006_ErlotinibRatio", min_value = 2.25)
paths_15 <- shortest.paths.to.target(ss15, target = "EGFR")

# cell line = HCC827, ExpSet = TenCell, Drug = Erlotinib, rep = 1

ss16 <- select.sites.w.min.value(gz.cf, "HCC827_ErlotinibRatio", min_value = 2.25)
paths_16 <- shortest.paths.to.target(ss16, target = "EGFR")


##### PR171
# cell line = H3122, ExpSet = SEPTM, Drug = PR171， rep = 3

ss17 <- select.sites.w.min.value(gz.cf, "H3122SEPTM.PR1.ratio", min_value = 2.25)
paths_17 <- shortest.paths.to.target(ss17, target = "")

ss18 <- select.sites.w.min.value(gz.cf, "H3122SEPTM.PR2.ratio", min_value = 2.25)
paths_18 <- shortest.paths.to.target(ss18, target = "")

ss19 <- select.sites.w.min.value(gz.cf, "H3122SEPTM.PR3.ratio", min_value = 2.25)
paths_19 <- shortest.paths.to.target(ss19, target = "")

# cell line = PC9, ExpSet = SEPTM, Drug = PR171， rep = 3

ss20 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.PR1.ratio", min_value = 2.25)
paths_20 <- shortest.paths.to.target(ss20, target = "")

ss21 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.PR2.ratio", min_value = 2.25)
paths_21 <- shortest.paths.to.target(ss21, target = "")

ss22 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.PR3.ratio", min_value = 2.25)
paths_22 <- shortest.paths.to.target(ss22, target = "")

##### Dasatinib
# cell line = H2286, ExpSet = TenCell, Drug = Dasatinib， rep = 1

ss23 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.PR1.ratio", min_value = 2.25)
paths_23 <- shortest.paths.to.target(ss23, target = "DDR2")

# cell line = H366, ExpSet = TenCell, Drug = Dasatinib， rep = 1

ss24 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.PR1.ratio", min_value = 2.25)
paths_24 <- shortest.paths.to.target(ss24, target = "DDR2")

##### Afatinib
# cell line = H1781, ExpSet = TenCell, Drug = Afatinib， rep = 1

ss25 <- select.sites.w.min.value(gz.cf, "PC9SEPTM.PR1.ratio", min_value = 2.25)
paths_25 <- shortest.paths.to.target(ss25, target = "HER2")
```
# The union and intersection or single path network
```{r}
### 123
#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_1 <- my.union(paths_1, paths_2, paths_3)
UN_1 <- graph.cfn.cccn (U_1, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_1 <- my.intersect(paths_1, paths_2, paths_3)
IN_1 <- graph.cfn.cccn (I_1, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()


### 45
#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_2 <- my.union(paths_4, paths_5)
UN_2 <- graph.cfn.cccn (U_2, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_2 <- my.intersect(paths_4, paths_5)
IN_2 <- graph.cfn.cccn (I_2, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()


### 67
#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_3 <- my.union(paths_6, paths_7)
UN_3 <- graph.cfn.cccn (U_3, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_3 <- my.intersect(paths_6, paths_7)
IN_3 <- graph.cfn.cccn (I_3, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 8
SU_1 <- my.union(paths_8)
N_1 <- graph.cfn.cccn (SU_1, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 9
SU_2 <- my.union(paths_8)
N_2 <- graph.cfn.cccn (SU_2, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 101112
#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_4 <- my.union(paths_10, paths_11, paths_12)
UN_4 <- graph.cfn.cccn (U_4, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_4 <- my.intersect(paths_10, paths_11, paths_12)
IN_4 <- graph.cfn.cccn (I_4, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 1314
#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_5 <- my.union(paths_13, paths_14)
UN_5 <- graph.cfn.cccn (U_5, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_5 <- my.intersect(paths_13, paths_14)
IN_5 <- graph.cfn.cccn (I_5, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 15
SU_3 <- my.union(paths_15)
N_3 <- graph.cfn.cccn (SU_3, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 16
SU_4 <- my.union(paths_16)
N_4 <- graph.cfn.cccn (SU_4, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 171819
#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_6 <- my.union(paths_17, paths_18, paths_19)
UN_6 <- graph.cfn.cccn (U_6, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_6 <- my.intersect(paths_17, paths_18, paths_19)
IN_6 <- graph.cfn.cccn (I_6, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 202122
#Find the union of shortest paths networks for the three SEPTM experiments and draw the network
U_7 <- my.union(paths_20, paths_21, paths_22)
UN_7 <- graph.cfn.cccn (U_7, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

#Find the intersection of shortest paths networks for the three SEPTM experiments
I_7 <- my.intersect(paths_20, paths_21, paths_22)
IN_7 <- graph.cfn.cccn (I_7, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 23
SU_5 <- my.union(paths_23)
N_5 <- graph.cfn.cccn (SU_5, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 24
SU_6 <- my.union(paths_24)
N_6 <- graph.cfn.cccn (SU_6, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

### 25
SU_1 <- my.union(paths_25)
N_7 <- graph.cfn.cccn (SU_7, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()
```


# This chunk selects sites for a particular cell line/drug combo that meet criteria for minimum number of observations, minimum absolute value of mean for the ratio, and maximun coefficient of variation for the ratio. Then it computes the shortest paths in the CFN from the selected sites to a specified target (e.g, the drug target) and draws the network. PC9/erlotinib is used as an example.  

```{r shortest paths to target for PC9/erlotinib-mean/CV method}
#There are 5 PC9/erlotinib experiments (3 from SEPTM and 2 from TenCellLines). Select sites that (i) have observed values in at least two experiments; (ii) have mean change of at least 2.25-fold; (iii) have a "small" standard deviation. Calculate the coefficient of variation for log-transformed data (https://en.wikipedia.org/wiki/Coefficient_of_variation). Select sites with CV<=1.

all_cols <- colnames(gz.cf)
all_cols

#Make a dataframe with just the following columns from gz.cf: id, Gene.Name and the 5 PC9/Erlotinib data columns
desired_cols <- c("id", "Gene.Name", "PC9SEPTM.E1.ratio", "PC9SEPTM.E2.ratio", "PC9SEPTM.E3.ratio", "PC9_Erlotinib.1Ratio", "PC9_ErlotinibRatio")

#Select the rows that have at least 2 (non-NA) observations
gz_pc9_erl.cf <- gz.cf[desired_cols]
gz_pc9_erl_keep.cf <- select.sites.w.enough.obs(gz_pc9_erl.cf, num_rep = 5, min_obs = 2)
nrow(gz_pc9_erl_keep.cf)

#Calculate the mean and keep only those rows with abs(mean) > log2(2.25)
gz_pc9_erl_keep2.cf <- select.sites.w.min.mean(gz_pc9_erl_keep.cf, first_rep = 3, num_rep = 5, min_mean = 2.25)
nrow(gz_pc9_erl_keep2.cf)

#Calculate the log-transformed coefficient of variation for each row and keep only rows with CV <=1
gz_pc9_erl_keep2.cf <- select.sites.w.max.cv(gz_pc9_erl_keep2.cf, first_rep = 3, num_rep =5, max_cv = 1)
nrow(gz_pc9_erl_keep2.cf)

#Now compute the shortest paths network for this set of sites and make Cytoscape graph.
gz_pc9_erl_keep2_paths <- shortest.paths.to.target(gz_pc9_erl_keep2.cf, target = "EGFR")
nrow(gz_pc9_erl_keep2_paths)
changed_genes_network <- graph.cfn.cccn (gz_pc9_erl_keep2_paths, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()


```  
# use the identical method to measure the H3122 cell lines sets
```{r}
#Make a dataframe with just the following columns from gz.cf: id, Gene.Name and the 5 H3122/Crizotinib data columns
desired_cols2 <- c("id", "Gene.Name", "H3122SEPTM.C1.ratio", "H3122SEPTM.C2.ratio", "H3122SEPTM.C3.ratio", "H3122_Crizotinib.1Ratio", "H3122CrizotinibRatio")

#Select the rows that have at least 2 (non-NA) observations
gz_H3_CRI.cf <- gz.cf[desired_cols2]
gz_H3_CRI_keep.cf <- select.sites.w.enough.obs(gz_H3_CRI.cf, num_rep = 5, min_obs = 2)
nrow(gz_H3_CRI_keep.cf)

#Calculate the mean and keep only those rows with abs(mean) > log2(2.25)
gz_pc9_erl_keep2.cf <- select.sites.w.min.mean(gz_pc9_erl_keep.cf, first_rep = 3, num_rep = 5, min_mean = 2.25)
nrow(gz_pc9_erl_keep2.cf)

#Calculate the log-transformed coefficient of variation for each row and keep only rows with CV <=1
gz_H3_CRI_keep2.cf <- select.sites.w.max.cv(gz_H3_CRI_keep2.cf, first_rep = 3, num_rep =5, max_cv = 1)
nrow(gz_H3_CRI_keep2.cf)

#Now compute the shortest paths network for this set of sites and make Cytoscape graph.
gz_H3_CRI_keep2_paths <- shortest.paths.to.target(gz_H3_CRI_keep2.cf, target = "EGFR")
nrow(gz_H3_CRI_keep2_paths)
changed_genes_network <- graph.cfn.cccn (gz_pc9_erl_keep2_paths, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()


```

```{r creating cell line name list}
gz_experiments_df <- read.csv("gz_experiments.csv")
cell_line <- gz_experiments_df$Column.6


```

# Heatmap comparison of shortest paths network
# Assumptions: In SPN, each nodes is a representative maker for the impact of drug (if no change, then no drug effect)
# Based on this assumpation, a target-based comparison would make more biological sense and give more clue about the overlapping pahtways
```{r target = MET/HGFR}
MET_paths_1 <- shortest.paths.to.target(ss1, target = "MET")
MET_paths_2 <- shortest.paths.to.target(ss2, target = "MET")
MET_paths_3 <- shortest.paths.to.target(ss3, target = "MET")
MET_paths_4 <- shortest.paths.to.target(ss4, target = "MET")
MET_paths_5 <- shortest.paths.to.target(ss5, target = "MET")
MET_paths_6 <- shortest.paths.to.target(ss6, target = "MET")
MET_paths_7 <- shortest.paths.to.target(ss7, target = "MET")
MET_paths_8 <- shortest.paths.to.target(ss8, target = "MET")
MET_paths_9 <- shortest.paths.to.target(ss9, target = "MET")
MET_paths_10 <- shortest.paths.to.target(ss10, target = "MET")
MET_paths_11 <- shortest.paths.to.target(ss11, target = "MET")
MET_paths_12 <- shortest.paths.to.target(ss12, target = "MET")
MET_paths_13 <- shortest.paths.to.target(ss13, target = "MET")
MET_paths_14 <- shortest.paths.to.target(ss14, target = "MET")
MET_paths_15 <- shortest.paths.to.target(ss15, target = "MET")
MET_paths_16 <- shortest.paths.to.target(ss16, target = "MET")
MET_paths_17 <- shortest.paths.to.target(ss17, target = "MET")
MET_paths_18 <- shortest.paths.to.target(ss18, target = "MET")
MET_paths_19 <- shortest.paths.to.target(ss19, target = "MET")
MET_paths_20 <- shortest.paths.to.target(ss20, target = "MET")
MET_paths_21 <- shortest.paths.to.target(ss21, target = "MET")
MET_paths_22 <- shortest.paths.to.target(ss22, target = "MET")
MET_paths_23 <- shortest.paths.to.target(ss23, target = "MET")
MET_paths_24 <- shortest.paths.to.target(ss24, target = "MET")
MET_paths_25 <- shortest.paths.to.target(ss25, target = "MET")

MET_intercet <- my.intersect(MET_paths_1,
MET_paths_2,
MET_paths_3,
MET_paths_4,
MET_paths_5,
MET_paths_6,
MET_paths_7,
MET_paths_8,
MET_paths_9,
MET_paths_10,
MET_paths_11,
MET_paths_12,
MET_paths_13,
MET_paths_14,
MET_paths_15,
MET_paths_16,
MET_paths_17,
MET_paths_18,
MET_paths_19,
MET_paths_20,
MET_paths_21,
MET_paths_22,
MET_paths_23,
MET_paths_24,
MET_paths_25)
MET_Network <- graph.cfn.cccn (MET_intercet, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()
MET_1_nrow_ratio <-nrow(MET_paths_1)/nrow(MET_intercet)
MET_2_nrow_ratio <-nrow(MET_paths_2)/nrow(MET_intercet)
MET_3_nrow_ratio <-nrow(MET_paths_3)/nrow(MET_intercet)
MET_4_nrow_ratio <-nrow(MET_paths_4)/nrow(MET_intercet)
MET_5_nrow_ratio <-nrow(MET_paths_5)/nrow(MET_intercet)
MET_6_nrow_ratio <-nrow(MET_paths_6)/nrow(MET_intercet)
MET_7_nrow_ratio <-nrow(MET_paths_7)/nrow(MET_intercet)
MET_8_nrow_ratio <-nrow(MET_paths_8)/nrow(MET_intercet)
MET_9_nrow_ratio <-nrow(MET_paths_9)/nrow(MET_intercet)
MET_10_nrow_ratio <-nrow(MET_paths_10)/nrow(MET_intercet)
MET_11_nrow_ratio <-nrow(MET_paths_11)/nrow(MET_intercet)
MET_12_nrow_ratio <-nrow(MET_paths_12)/nrow(MET_intercet)
MET_13_nrow_ratio <-nrow(MET_paths_13)/nrow(MET_intercet)
MET_14_nrow_ratio <-nrow(MET_paths_14)/nrow(MET_intercet)
MET_15_nrow_ratio <-nrow(MET_paths_15)/nrow(MET_intercet)
MET_16_nrow_ratio <-nrow(MET_paths_16)/nrow(MET_intercet)
MET_17_nrow_ratio <-nrow(MET_paths_17)/nrow(MET_intercet)
MET_18_nrow_ratio <-nrow(MET_paths_18)/nrow(MET_intercet)
MET_19_nrow_ratio <-nrow(MET_paths_19)/nrow(MET_intercet)
MET_20_nrow_ratio <-nrow(MET_paths_20)/nrow(MET_intercet)
MET_21_nrow_ratio <-nrow(MET_paths_21)/nrow(MET_intercet)
MET_22_nrow_ratio <-nrow(MET_paths_22)/nrow(MET_intercet)
MET_23_nrow_ratio <-nrow(MET_paths_23)/nrow(MET_intercet)
MET_24_nrow_ratio <-nrow(MET_paths_24)/nrow(MET_intercet)
MET_25_nrow_ratio <-nrow(MET_paths_25)/nrow(MET_intercet)

#creating the ratio column
MET_ratios <- c(MET_1_nrow_ratio,
MET_2_nrow_ratio,
MET_3_nrow_ratio,
MET_4_nrow_ratio,
MET_5_nrow_ratio,
MET_6_nrow_ratio,
MET_7_nrow_ratio,
MET_8_nrow_ratio,
MET_9_nrow_ratio,
MET_10_nrow_ratio,
MET_11_nrow_ratio,
MET_12_nrow_ratio,
MET_13_nrow_ratio,
MET_14_nrow_ratio,
MET_15_nrow_ratio,
MET_16_nrow_ratio,
MET_17_nrow_ratio,
MET_18_nrow_ratio,
MET_19_nrow_ratio,
MET_20_nrow_ratio,
MET_21_nrow_ratio,
MET_22_nrow_ratio,
MET_23_nrow_ratio,
MET_24_nrow_ratio,
MET_25_nrow_ratio)

#creatign a dataframe to generate the heatmap
MET_dataframe <- data.frame(MET_ratios)
MET_dataframe <- t(MET_dataframe)
colnames(MET_dataframe) <- cell_line
write.table(MET_dataframe,"MET.txt")
rownames(MET) <- MET$X
MET <- MET[2:26]
pheatmap::pheatmap(MET)


```

```{r target = EGFR}
EGFR_paths_1 <- shortest.paths.to.target(ss1, target = "EGFR")
EGFR_paths_2 <- shortest.paths.to.target(ss2, target = "EGFR")
EGFR_paths_3 <- shortest.paths.to.target(ss3, target = "EGFR")
EGFR_paths_4 <- shortest.paths.to.target(ss4, target = "EGFR")
EGFR_paths_5 <- shortest.paths.to.target(ss5, target = "EGFR")
EGFR_paths_6 <- shortest.paths.to.target(ss6, target = "EGFR")
EGFR_paths_7 <- shortest.paths.to.target(ss7, target = "EGFR")
EGFR_paths_8 <- shortest.paths.to.target(ss8, target = "EGFR")
EGFR_paths_9 <- shortest.paths.to.target(ss9, target = "EGFR")
EGFR_paths_10 <- shortest.paths.to.target(ss10, target = "EGFR")
EGFR_paths_11 <- shortest.paths.to.target(ss11, target = "EGFR")
EGFR_paths_12 <- shortest.paths.to.target(ss12, target = "EGFR")
EGFR_paths_13 <- shortest.paths.to.target(ss13, target = "EGFR")
EGFR_paths_14 <- shortest.paths.to.target(ss14, target = "EGFR")
EGFR_paths_15 <- shortest.paths.to.target(ss15, target = "EGFR")
EGFR_paths_16 <- shortest.paths.to.target(ss16, target = "EGFR")
EGFR_paths_17 <- shortest.paths.to.target(ss17, target = "EGFR")
EGFR_paths_18 <- shortest.paths.to.target(ss18, target = "EGFR")
EGFR_paths_19 <- shortest.paths.to.target(ss19, target = "EGFR")
EGFR_paths_20 <- shortest.paths.to.target(ss20, target = "EGFR")
EGFR_paths_21 <- shortest.paths.to.target(ss21, target = "EGFR")
EGFR_paths_22 <- shortest.paths.to.target(ss22, target = "EGFR")
EGFR_paths_23 <- shortest.paths.to.target(ss23, target = "EGFR")
EGFR_paths_24 <- shortest.paths.to.target(ss24, target = "EGFR")
EGFR_paths_25 <- shortest.paths.to.target(ss25, target = "EGFR")
EGFR_intercet <- my.intersect(EGFR_paths_1,
EGFR_paths_2,
EGFR_paths_3,
EGFR_paths_4,
EGFR_paths_5,
EGFR_paths_6,
EGFR_paths_7,
EGFR_paths_8,
EGFR_paths_9,
EGFR_paths_10,
EGFR_paths_11,
EGFR_paths_12,
EGFR_paths_13,
EGFR_paths_14,
EGFR_paths_15,
EGFR_paths_16,
EGFR_paths_17,
EGFR_paths_18,
EGFR_paths_19,
EGFR_paths_20,
EGFR_paths_21,
EGFR_paths_22,
EGFR_paths_23,
EGFR_paths_24,
EGFR_paths_25)
EGFR_Network <- graph.cfn.cccn (EGFR_intercet, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()
# 
EGFR_1_nrow_ratio <-nrow(EGFR_paths_1)/nrow(EGFR_intercet)
EGFR_2_nrow_ratio <-nrow(EGFR_paths_2)/nrow(EGFR_intercet)
EGFR_3_nrow_ratio <-nrow(EGFR_paths_3)/nrow(EGFR_intercet)
EGFR_4_nrow_ratio <-nrow(EGFR_paths_4)/nrow(EGFR_intercet)
EGFR_5_nrow_ratio <-nrow(EGFR_paths_5)/nrow(EGFR_intercet)
EGFR_6_nrow_ratio <-nrow(EGFR_paths_6)/nrow(EGFR_intercet)
EGFR_7_nrow_ratio <-nrow(EGFR_paths_7)/nrow(EGFR_intercet)
EGFR_8_nrow_ratio <-nrow(EGFR_paths_8)/nrow(EGFR_intercet)
EGFR_9_nrow_ratio <-nrow(EGFR_paths_9)/nrow(EGFR_intercet)
EGFR_10_nrow_ratio <-nrow(EGFR_paths_10)/nrow(EGFR_intercet)
EGFR_11_nrow_ratio <-nrow(EGFR_paths_11)/nrow(EGFR_intercet)
EGFR_12_nrow_ratio <-nrow(EGFR_paths_12)/nrow(EGFR_intercet)
EGFR_13_nrow_ratio <-nrow(EGFR_paths_13)/nrow(EGFR_intercet)
EGFR_14_nrow_ratio <-nrow(EGFR_paths_14)/nrow(EGFR_intercet)
EGFR_15_nrow_ratio <-nrow(EGFR_paths_15)/nrow(EGFR_intercet)
EGFR_16_nrow_ratio <-nrow(EGFR_paths_16)/nrow(EGFR_intercet)
EGFR_17_nrow_ratio <-nrow(EGFR_paths_17)/nrow(EGFR_intercet)
EGFR_18_nrow_ratio <-nrow(EGFR_paths_18)/nrow(EGFR_intercet)
EGFR_19_nrow_ratio <-nrow(EGFR_paths_19)/nrow(EGFR_intercet)
EGFR_20_nrow_ratio <-nrow(EGFR_paths_20)/nrow(EGFR_intercet)
EGFR_21_nrow_ratio <-nrow(EGFR_paths_21)/nrow(EGFR_intercet)
EGFR_22_nrow_ratio <-nrow(EGFR_paths_22)/nrow(EGFR_intercet)
EGFR_23_nrow_ratio <-nrow(EGFR_paths_23)/nrow(EGFR_intercet)
EGFR_24_nrow_ratio <-nrow(EGFR_paths_24)/nrow(EGFR_intercet)
EGFR_25_nrow_ratio <-nrow(EGFR_paths_25)/nrow(EGFR_intercet)

EGFR_ratios <- c(EGFR_1_nrow_ratio,
EGFR_2_nrow_ratio,
EGFR_3_nrow_ratio,
EGFR_4_nrow_ratio,
EGFR_5_nrow_ratio,
EGFR_6_nrow_ratio,
EGFR_7_nrow_ratio,
EGFR_8_nrow_ratio,
EGFR_9_nrow_ratio,
EGFR_10_nrow_ratio,
EGFR_11_nrow_ratio,
EGFR_12_nrow_ratio,
EGFR_13_nrow_ratio,
EGFR_14_nrow_ratio,
EGFR_15_nrow_ratio,
EGFR_16_nrow_ratio,
EGFR_17_nrow_ratio,
EGFR_18_nrow_ratio,
EGFR_19_nrow_ratio,
EGFR_20_nrow_ratio,
EGFR_21_nrow_ratio,
EGFR_22_nrow_ratio,
EGFR_23_nrow_ratio,
EGFR_24_nrow_ratio,
EGFR_25_nrow_ratio)

#creatign a dataframe to generate the heatmap
EGFR_dataframe <- data.frame(EGFR_ratios)
EGFR_dataframe <- t(EGFR_dataframe)
colnames(EGFR_dataframe) <- cell_line
write.table(EGFR_dataframe,"EGFR.txt")
EGFR <-read.csv("EGFR.csv")
rownames(EGFR) <- EGFR$X
EGFR <- EGFR[2:26]
pheatmap::pheatmap(EGFR)

```


```{r target = ALK}
ALK_paths_1 <- shortest.paths.to.target(ss1, target = "ALK")
ALK_paths_2 <- shortest.paths.to.target(ss2, target = "ALK")
ALK_paths_3 <- shortest.paths.to.target(ss3, target = "ALK")
ALK_paths_4 <- shortest.paths.to.target(ss4, target = "ALK")
ALK_paths_5 <- shortest.paths.to.target(ss5, target = "ALK")
ALK_paths_6 <- shortest.paths.to.target(ss6, target = "ALK")
ALK_paths_7 <- shortest.paths.to.target(ss7, target = "ALK")
ALK_paths_8 <- shortest.paths.to.target(ss8, target = "ALK")
ALK_paths_9 <- shortest.paths.to.target(ss9, target = "ALK")
ALK_paths_10 <- shortest.paths.to.target(ss10, target = "ALK")
ALK_paths_11 <- shortest.paths.to.target(ss11, target = "ALK")
ALK_paths_12 <- shortest.paths.to.target(ss12, target = "ALK")
ALK_paths_13 <- shortest.paths.to.target(ss13, target = "ALK")
ALK_paths_14 <- shortest.paths.to.target(ss14, target = "ALK")
ALK_paths_15 <- shortest.paths.to.target(ss15, target = "ALK")
ALK_paths_16 <- shortest.paths.to.target(ss16, target = "ALK")
ALK_paths_17 <- shortest.paths.to.target(ss17, target = "ALK")
ALK_paths_18 <- shortest.paths.to.target(ss18, target = "ALK")
ALK_paths_19 <- shortest.paths.to.target(ss19, target = "ALK")
ALK_paths_20 <- shortest.paths.to.target(ss20, target = "ALK")
ALK_paths_21 <- shortest.paths.to.target(ss21, target = "ALK")
ALK_paths_22 <- shortest.paths.to.target(ss22, target = "ALK")
ALK_paths_23 <- shortest.paths.to.target(ss23, target = "ALK")
ALK_paths_24 <- shortest.paths.to.target(ss24, target = "ALK")
ALK_paths_25 <- shortest.paths.to.target(ss25, target = "ALK")
ALK_intercet <- my.intersect(ALK_paths_1,
ALK_paths_2,
ALK_paths_3,
ALK_paths_4,
ALK_paths_5,
ALK_paths_6,
ALK_paths_7,
ALK_paths_8,
ALK_paths_9,
ALK_paths_10,
ALK_paths_11,
ALK_paths_12,
ALK_paths_13,
ALK_paths_14,
ALK_paths_15,
ALK_paths_16,
ALK_paths_17,
ALK_paths_18,
ALK_paths_19,
ALK_paths_20,
ALK_paths_21,
ALK_paths_22,
ALK_paths_23,
ALK_paths_24,
ALK_paths_25)
ALK_Network <- graph.cfn.cccn (ALK_intercet, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

ALK_1_nrow_ratio <-nrow(ALK_paths_1)/nrow(ALK_intercet)
ALK_2_nrow_ratio <-nrow(ALK_paths_2)/nrow(ALK_intercet)
ALK_3_nrow_ratio <-nrow(ALK_paths_3)/nrow(ALK_intercet)
ALK_4_nrow_ratio <-nrow(ALK_paths_4)/nrow(ALK_intercet)
ALK_5_nrow_ratio <-nrow(ALK_paths_5)/nrow(ALK_intercet)
ALK_6_nrow_ratio <-nrow(ALK_paths_6)/nrow(ALK_intercet)
ALK_7_nrow_ratio <-nrow(ALK_paths_7)/nrow(ALK_intercet)
ALK_8_nrow_ratio <-nrow(ALK_paths_8)/nrow(ALK_intercet)
ALK_9_nrow_ratio <-nrow(ALK_paths_9)/nrow(ALK_intercet)
ALK_10_nrow_ratio <-nrow(ALK_paths_10)/nrow(ALK_intercet)
ALK_11_nrow_ratio <-nrow(ALK_paths_11)/nrow(ALK_intercet)
ALK_12_nrow_ratio <-nrow(ALK_paths_12)/nrow(ALK_intercet)
ALK_13_nrow_ratio <-nrow(ALK_paths_13)/nrow(ALK_intercet)
ALK_14_nrow_ratio <-nrow(ALK_paths_14)/nrow(ALK_intercet)
ALK_15_nrow_ratio <-nrow(ALK_paths_15)/nrow(ALK_intercet)
ALK_16_nrow_ratio <-nrow(ALK_paths_16)/nrow(ALK_intercet)
ALK_17_nrow_ratio <-nrow(ALK_paths_17)/nrow(ALK_intercet)
ALK_18_nrow_ratio <-nrow(ALK_paths_18)/nrow(ALK_intercet)
ALK_19_nrow_ratio <-nrow(ALK_paths_19)/nrow(ALK_intercet)
ALK_20_nrow_ratio <-nrow(ALK_paths_20)/nrow(ALK_intercet)
ALK_21_nrow_ratio <-nrow(ALK_paths_21)/nrow(ALK_intercet)
ALK_22_nrow_ratio <-nrow(ALK_paths_22)/nrow(ALK_intercet)
ALK_23_nrow_ratio <-nrow(ALK_paths_23)/nrow(ALK_intercet)
ALK_24_nrow_ratio <-nrow(ALK_paths_24)/nrow(ALK_intercet)
ALK_25_nrow_ratio <-nrow(ALK_paths_25)/nrow(ALK_intercet)

ALK_ratios <- c(ALK_1_nrow_ratio,
ALK_2_nrow_ratio,
ALK_3_nrow_ratio,
ALK_4_nrow_ratio,
ALK_5_nrow_ratio,
ALK_6_nrow_ratio,
ALK_7_nrow_ratio,
ALK_8_nrow_ratio,
ALK_9_nrow_ratio,
ALK_10_nrow_ratio,
ALK_11_nrow_ratio,
ALK_12_nrow_ratio,
ALK_13_nrow_ratio,
ALK_14_nrow_ratio,
ALK_15_nrow_ratio,
ALK_16_nrow_ratio,
ALK_17_nrow_ratio,
ALK_18_nrow_ratio,
ALK_19_nrow_ratio,
ALK_20_nrow_ratio,
ALK_21_nrow_ratio,
ALK_22_nrow_ratio,
ALK_23_nrow_ratio,
ALK_24_nrow_ratio,
ALK_25_nrow_ratio)

#creatign a dataframe to generate the heatmap
ALK_dataframe <- data.frame(ALK_ratios)
ALK_dataframe <- t(ALK_dataframe)
colnames(ALK_dataframe) <- cell_line
write.table(ALK_dataframe,"ALK.txt")
ALK <-read.csv("ALK.csv")
rownames(ALK) <- ALK$X
ALK <- ALK[2:26]
pheatmap::pheatmap(ALK)


```


```{r target = ROS1}
ROS1_paths_1 <- shortest.paths.to.target(ss1, target = "ROS1")
ROS1_paths_2 <- shortest.paths.to.target(ss2, target = "ROS1")
ROS1_paths_3 <- shortest.paths.to.target(ss3, target = "ROS1")
ROS1_paths_4 <- shortest.paths.to.target(ss4, target = "ROS1")
ROS1_paths_5 <- shortest.paths.to.target(ss5, target = "ROS1")
ROS1_paths_6 <- shortest.paths.to.target(ss6, target = "ROS1")
ROS1_paths_7 <- shortest.paths.to.target(ss7, target = "ROS1")
ROS1_paths_8 <- shortest.paths.to.target(ss8, target = "ROS1")
ROS1_paths_9 <- shortest.paths.to.target(ss9, target = "ROS1")
ROS1_paths_10 <- shortest.paths.to.target(ss10, target = "ROS1")
ROS1_paths_11 <- shortest.paths.to.target(ss11, target = "ROS1")
ROS1_paths_12 <- shortest.paths.to.target(ss12, target = "ROS1")
ROS1_paths_13 <- shortest.paths.to.target(ss13, target = "ROS1")
ROS1_paths_14 <- shortest.paths.to.target(ss14, target = "ROS1")
ROS1_paths_15 <- shortest.paths.to.target(ss15, target = "ROS1")
ROS1_paths_16 <- shortest.paths.to.target(ss16, target = "ROS1")
ROS1_paths_17 <- shortest.paths.to.target(ss17, target = "ROS1")
ROS1_paths_18 <- shortest.paths.to.target(ss18, target = "ROS1")
ROS1_paths_19 <- shortest.paths.to.target(ss19, target = "ROS1")
ROS1_paths_20 <- shortest.paths.to.target(ss20, target = "ROS1")
ROS1_paths_21 <- shortest.paths.to.target(ss21, target = "ROS1")
ROS1_paths_22 <- shortest.paths.to.target(ss22, target = "ROS1")
ROS1_paths_23 <- shortest.paths.to.target(ss23, target = "ROS1")
ROS1_paths_24 <- shortest.paths.to.target(ss24, target = "ROS1")
ROS1_paths_25 <- shortest.paths.to.target(ss25, target = "ROS1")

ROS1_intercet <- my.intersect(ROS1_paths_1,
ROS1_paths_2,
ROS1_paths_3,
ROS1_paths_4,
ROS1_paths_5,
ROS1_paths_6,
ROS1_paths_7,
ROS1_paths_8,
ROS1_paths_9,
ROS1_paths_10,
ROS1_paths_11,
ROS1_paths_12,
ROS1_paths_13,
ROS1_paths_14,
ROS1_paths_15,
ROS1_paths_16,
ROS1_paths_17,
ROS1_paths_18,
ROS1_paths_19,
ROS1_paths_20,
ROS1_paths_21,
ROS1_paths_22,
ROS1_paths_23,
ROS1_paths_24,
ROS1_paths_25)
ROS1_Network <- graph.cfn.cccn (ROS1_intercet, ld=FALSE, gz=TRUE, only.cfn=TRUE)
all.ratio.styles()

ROS1_1_nrow_ratio <-nrow(ROS1_paths_1)/nrow(ROS1_intercet)
ROS1_2_nrow_ratio <-nrow(ROS1_paths_2)/nrow(ROS1_intercet)
ROS1_3_nrow_ratio <-nrow(ROS1_paths_3)/nrow(ROS1_intercet)
ROS1_4_nrow_ratio <-nrow(ROS1_paths_4)/nrow(ROS1_intercet)
ROS1_5_nrow_ratio <-nrow(ROS1_paths_5)/nrow(ROS1_intercet)
ROS1_6_nrow_ratio <-nrow(ROS1_paths_6)/nrow(ROS1_intercet)
ROS1_7_nrow_ratio <-nrow(ROS1_paths_7)/nrow(ROS1_intercet)
ROS1_8_nrow_ratio <-nrow(ROS1_paths_8)/nrow(ROS1_intercet)
ROS1_9_nrow_ratio <-nrow(ROS1_paths_9)/nrow(ROS1_intercet)
ROS1_10_nrow_ratio <-nrow(ROS1_paths_10)/nrow(ROS1_intercet)
ROS1_11_nrow_ratio <-nrow(ROS1_paths_11)/nrow(ROS1_intercet)
ROS1_12_nrow_ratio <-nrow(ROS1_paths_12)/nrow(ROS1_intercet)
ROS1_13_nrow_ratio <-nrow(ROS1_paths_13)/nrow(ROS1_intercet)
ROS1_14_nrow_ratio <-nrow(ROS1_paths_14)/nrow(ROS1_intercet)
ROS1_15_nrow_ratio <-nrow(ROS1_paths_15)/nrow(ROS1_intercet)
ROS1_16_nrow_ratio <-nrow(ROS1_paths_16)/nrow(ROS1_intercet)
ROS1_17_nrow_ratio <-nrow(ROS1_paths_17)/nrow(ROS1_intercet)
ROS1_18_nrow_ratio <-nrow(ROS1_paths_18)/nrow(ROS1_intercet)
ROS1_19_nrow_ratio <-nrow(ROS1_paths_19)/nrow(ROS1_intercet)
ROS1_20_nrow_ratio <-nrow(ROS1_paths_20)/nrow(ROS1_intercet)
ROS1_21_nrow_ratio <-nrow(ROS1_paths_21)/nrow(ROS1_intercet)
ROS1_22_nrow_ratio <-nrow(ROS1_paths_22)/nrow(ROS1_intercet)
ROS1_23_nrow_ratio <-nrow(ROS1_paths_23)/nrow(ROS1_intercet)
ROS1_24_nrow_ratio <-nrow(ROS1_paths_24)/nrow(ROS1_intercet)
ROS1_25_nrow_ratio <-nrow(ROS1_paths_25)/nrow(ROS1_intercet)

ROS1_ratios <- c(ROS1_1_nrow_ratio,
ROS1_2_nrow_ratio,
ROS1_3_nrow_ratio,
ROS1_4_nrow_ratio,
ROS1_5_nrow_ratio,
ROS1_6_nrow_ratio,
ROS1_7_nrow_ratio,
ROS1_8_nrow_ratio,
ROS1_9_nrow_ratio,
ROS1_10_nrow_ratio,
ROS1_11_nrow_ratio,
ROS1_12_nrow_ratio,
ROS1_13_nrow_ratio,
ROS1_14_nrow_ratio,
ROS1_15_nrow_ratio,
ROS1_16_nrow_ratio,
ROS1_17_nrow_ratio,
ROS1_18_nrow_ratio,
ROS1_19_nrow_ratio,
ROS1_20_nrow_ratio,
ROS1_21_nrow_ratio,
ROS1_22_nrow_ratio,
ROS1_23_nrow_ratio,
ROS1_24_nrow_ratio,
ROS1_25_nrow_ratio)

#creatign a dataframe to generate the heatmap
ROS1_dataframe <- data.frame(ROS1_ratios)
ROS1_dataframe <- t(ROS1_dataframe)
colnames(ROS1_dataframe) <- cell_line
write.table(ROS1_dataframe,"ROS1.txt")




```


When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

